### 2018-01-03 R/manuscript_jep_hpp.Rmd
Add files via upload

---
title: "manuscript - JEP:HPP"
author: "Filip Dechterenko"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

## Load libraries

```{r load libraries}
library(tidyverse); theme_set(theme_bw(16))
library(ez)
library(psyphy)

source("tools.R")

```

# Experiment 1

```{r load data - exp 1}
load("../data/exp1/responses/responses_150330.RData")

df_exp1 <- filter(df, block != 0)

participants_exp1 <- read.csv("../data/exp1/participants_150526.csv")

# originally, we colledcted three levels of variaiblity, but the condition with kappa=64 showed similar results as kappa = 16
df_exp1 <- filter(df_exp1, restk != "64") %>% as_data_frame()
```

## Participant info
```{r}
table(participants_exp1$gender)
c(mean(participants_exp1$age), sd(participants_exp1$age)) %>% round(2)
```

## Results

```{r}
df_exp1 %>% group_by(restk) %>% summarize(accuracy_mean = mean(accuracy, na.rm = T) %>% round(2))
```

## Figure 1

```{r Figure 1}
traj_k64 <- read.table("../data/exp1/trajectories/T001_64_rest4.csv") %>% select(x = V1,y = V2) %>% as_data_frame()
p1 <- traj_k64 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15) +
  ggtitle("Ballistic-like")

traj_k4 <- read.table("../data/exp1/trajectories/T001_4_rest4.csv") %>% select(x = V3,y = V4) %>% as_data_frame()
p2 <- traj_k4 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15)+
  ggtitle("Brownian-like")
gridExtra::grid.arrange(p1,p2, ncol = 2)
ggsave("Figure1_ballistic.png", p1, width = 6, height = 6)
ggsave("Figure1_brownian.png", p2, width = 6, height = 6)
ggsave("Figure1_ballistic.eps", p1, width = 6, height = 6)
ggsave("Figure1_brownian.eps", p2, width = 6, height = 6)
```

## Figure 2

```{r Figure 2}
p1 <- df_exp1 %>%
  filter(restk == 4) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,8,16,32,64,128),labels = c("1","8","16","32","64","128"), trans = "log2") + 
  geom_vline(xintercept = 4, linetype = 2) +
  ggtitle("Brownian-like-distractors")
p2 <- df_exp1 %>%
  filter(restk == 16) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1)  + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,8,16,32,64,128),labels = c("1","8","16","32","64","128"), trans = "log2") + 
  geom_vline(xintercept = 16, linetype = 2) +
  ggtitle("Ballistic-like-distractors")
gridExtra::grid.arrange(p1,p2, ncol = 2)

ggsave("plots/Figure2_brownian.png", p1, width = 6, height = 6)
ggsave("plots/Figure2_ballistic.png", p2, width = 6, height = 6)
ggsave("plots/Figure2_brownian.eps", p1, width = 6, height = 6)
ggsave("plots/Figure2_ballistic.eps", p2, width = 6, height = 6)
```

```{r fitting weibull}

df.pf <- filter(df_exp1, restk == 16, type %in% c(2,4,8,16,32))
df.pf$type <- as.numeric(levels(df.pf$type))[df.pf$type]

df.pf2 <- df.pf %>% group_by(type) %>% summarise(yes = sum(accuracy), no = n()-sum(accuracy),accuracy=1-mean(accuracy))

pf <- psyfun.2asym(cbind(yes, no) ~ type,data = df.pf2, link = weib.2asym, init.g = 0.125, init.lam = 0.05 )   
x <- seq(-2,32,0.01)
y <- predict(pf, data.frame(type = x), type="response")

dfmodel <- data.frame(x,y)

p <- ggplot(data = dfmodel, aes(x = x, y = y)) + geom_line(color="red", size =1.5) + stat_summary(data = df.pf, aes(x = type, y=accuracy),fun.data = "mean_cl_boot", size = 1) + scale_x_continuous(expression("Target's"~kappa), breaks = df.pf2$type) + ylab("Accuracy")
p

```

Test with baseline

```{r}
df_exp1 %>% group_by(type, restk,subject) %>% summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>% filter(accuracy <1) %>% do(t.test(.$accuracy, mu = .125) %>% broom::tidy()) %>% mutate(p.value = round(p.value, 3)) %>% knitr::kable()
```

Difference between symmetrical cases
```{r}
df.sym <- df_exp1 %>% filter((restk == 4 & type == 16) |(restk == 16 & type == 4))
ez::ezANOVA(df.sym,
        dv=accuracy,
        wid = subject,
        within = restk)
```

# Experiment 2

```{r load data - experiment 2}
load("../data/exp1_fin/responses/responses_150622.RData")
df_exp2 <- filter(df, block != 0)

participants_exp2 <- read.csv("../data/exp1_fin/participants_150526.csv", fileEncoding = "UTF8")

df2_exp2 <- rbind(df_exp2,df_exp2)
df2_exp2$version <- 2
df2_exp2$version[1:nrow(df_exp2)] <- 1

# this is a little hack, just to make a correct ggplot with one line
tmp <- df_exp2$restk
df2_exp2$restk[df2_exp2$version == 2] <- df_exp2$type
df2_exp2$type[df2_exp2$version == 2] <- tmp

df2_exp2$version <- factor(df2_exp2$version, labels = c("fix distractors' k", "fix target's k"))
```

## Participant info
```{r}
table(participants_exp2$gender)
c(mean(participants_exp2$age), sd(participants_exp2$age)) %>% round(2)
```

## Figure 3

```{r plots experiment 2}

p_k2 <- df2_exp2 %>%
  filter(restk == 2) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous(expression(kappa~"of the others (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
  scale_linetype_manual(values = c(2,1)) +
  geom_vline(xintercept = 2, linetype = 2) +
  ggtitle(expression("Fixed "~kappa~"= 2"))

p_k4 <- df2_exp2 %>%
  filter(restk == 4) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous(expression(kappa~"of the others (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
  scale_linetype_manual(values = c(2,1)) +
  geom_vline(xintercept = 4, linetype = 2) +
  ggtitle(expression("Fixed "~kappa~"= 4"))

p_k8 <- df2_exp2 %>%
  filter(restk == 8) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous(expression(kappa~"of the others (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
  scale_linetype_manual(values = c(2,1)) +
  geom_vline(xintercept = 8, linetype = 2) +
  ggtitle(expression("Fixed "~kappa~"= 8"))

p_k16 <- df2_exp2 %>%
  filter(restk == 16) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous(expression(kappa~"of the others (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
  scale_linetype_manual(values = c(2,1)) +
  geom_vline(xintercept = 16, linetype = 2) +
  ggtitle(expression("Fixed "~kappa~"= 16"))

p_k64 <- df2_exp2 %>%
  filter(restk == 64) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous(expression(kappa~"of the others (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
  scale_linetype_manual(values = c(2,1)) +
  geom_vline(xintercept = 64, linetype = 2) +
  ggtitle(expression("Fixed "~kappa~"= 64"))

p_k64_legend <- df2_exp2 %>%
  filter(restk == 64) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous(expression(kappa~"of the others (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
  scale_linetype_manual(values = c(2,1)) +
  geom_vline(xintercept = 64, linetype = 2) +
  ggtitle(expression("Fixed "~kappa~"= 64"))

gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 5)
ggsave("plots/Fig3_k2.eps", p_k2, width = 6, height = 6)
ggsave("plots/Fig3_k4.eps", p_k4, width = 6, height = 6)
ggsave("plots/Fig3_k8.eps", p_k8, width = 6, height = 6)
ggsave("plots/Fig3_k16.eps", p_k16, width = 6, height = 6)
ggsave("plots/Fig3_k64.eps", p_k64, width = 6, height = 6)
ggsave("plots/Fig3_k64_legend.eps", p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

## Compute the asymmetry

```{r compute the assymetry, warning=F}
df3_exp2 <- df2_exp2 %>% group_by(type, restk) %>% do(p=compute.p(.))

df3_exp2$p <- unlist(df3_exp2$p) %>% round(3)
df4_exp2 <- df2_exp2 %>% group_by(type, restk) %>% do(ges=compute.des(.))
df4_exp2$ges <- unlist(df4_exp2$ges) %>% round(2)
df3_exp2$ges <- df4_exp2$ges

df5_exp2 <- df2_exp2 %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
  group_by(type, restk) %>%
  summarize(acc_diff = accuracy[version == "fix distractors' k"] - accuracy[version == "fix target's k"])

m <- matrix(df3_exp2$ges, nrow = 5)
rownames(m) <- levels(df_exp2$type)
colnames(m) <- levels(df_exp2$type)
m[upper.tri(m,diag = T)] <- NA

df3_exp2$ges <- as.vector(m)

m <- matrix(df3_exp2$p, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp2$p <- as.vector(m)

m <- matrix(df5_exp2$acc_diff, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp2$acc_diff <- as.vector(m)

df3_exp2$target_lower_than_dist <- df3_exp2$acc_diff < 0
df3_exp2 %>% filter(target_lower_than_dist)

df3_exp2 %>% filter(p < .05)
```

Test with baseline

```{r}
df_exp2 %>% group_by(type, restk,subject) %>% summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>% filter(accuracy <1) %>% do(t.test(.$accuracy, mu = .125) %>% broom::tidy()) %>% mutate(p.value = round(p.value, 3)) %>% knitr::kable()
```

# Experiment 3

```{r load data - exp 3}
load("../data/exp2/responses/responses_150410.RData")
df_exp3 <- filter(df, block != 0) 
df_exp3 <- df_exp3 %>% mutate(restk = restk * 100, type = type * 100)
participants <- read.csv("../data/exp2/participants_171023.csv")
```

## Participant info
```{r exp3 participant info}
table(participants_exp3$gender)
c(mean(participants_exp3$age), sd(participants_exp3$age)) %>% round(2)
```

## Results

```{r}
df_exp3 %>% group_by(restk) %>% summarize(accuracy_mean = mean(accuracy, na.rm = T) %>% round(2))
```

## Figure 4

```{r}
p1 <- df_exp3 %>%
  filter(restk == 2) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  geom_vline(xintercept = 2, linetype = 2) +
  scale_x_continuous("Target's speed (log scale)",breaks = c(0.5,1,2,3,4,6,8),labels = c("0.5","1","2","3","4","6","8"), trans = "log2") + 
  ggtitle("Slow-moving-distractors")
p2 <- df_exp3 %>%
  filter(restk == 4) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1)  + 
  ylab("Accuracy") + 
  ylim(0,1)+
  geom_vline(xintercept = 4, linetype = 2) +
  scale_x_continuous("Target's speed (log scale)",breaks = c(0.5,1,2,3,4,6,8),labels = c("0.5","1","2","3","4","6","8"), trans = "log2") + 
  ggtitle("Fast-moving-distractors")
gridExtra::grid.arrange(p1,p2, ncol = 2)

ggsave("plots/Figure4_slow.png", p1, width = 6, height = 6)
ggsave("plots/Figure4_fast.png", p2, width = 6, height = 6)
ggsave("plots/Figure4_slow.eps", p1, width = 6, height = 6)
ggsave("plots/Figure4_fast.eps", p2, width = 6, height = 6)
```

## Statistics

```{r exp 3 - statistics}
df_exp3 %>% group_by(restk) %>% summarize(acc = mean(accuracy) * 100, sd = sd(accuracy) *100)
```

```{r exp 3 - symmetric conditions}
df_cond1 <- df_exp3 %>% filter(type == 2 & restk == 4)
df_cond2 <- df_exp3 %>% filter(type == 4 & restk == 2) 
```

Difference between symmetrical cases
```{r}
df_sym <- df_exp3 %>% filter((restk == 2 & type == 4) |(restk == 4 & type == 2))
ez::ezANOVA(df_sym,
        dv=accuracy,
        wid = subject,
        within = restk)
ez::ezStats(df_sym,
        dv=accuracy,
        wid = subject,
        within = restk)

```

Test with baseline

```{r}
df_exp3 %>% group_by(type, restk,subject) %>% summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>% filter(accuracy <1) %>% do(t.test(.$accuracy, mu = .125) %>% broom::tidy()) %>% mutate(p.value = round(p.value, 3)) %>% knitr::kable()
```

# Experiment 4

```{r load data - exp 4}
load("../data/exp2_fin/responses/responses_171023.RData")

df_exp4 <- filter(df, block != 0) 
df_exp4 <- df_exp4 %>% mutate(restk = restk * 100, type = type * 100)
rm(df)

participants_exp4 <- read.csv("../data/exp2_fin/participants_171023.csv")

df2_exp4 <- rbind(df_exp4, df_exp4)
df2_exp4$version <- 2
df2_exp4$version[1:nrow(df_exp4)] <- 1

# this is a little hack, just to make a correct ggplot with one line
tmp <- df_exp4$restk
df2_exp4$restk[df2_exp4$version == 2] <- df_exp4$type
df2_exp4$type[df2_exp4$version == 2] <- tmp

df2_exp4$version <- factor(df2_exp4$version, labels = c("fix distractors' speed", "fix target's speed"))
```

## Participant info
```{r exp4 - participants info}
table(participants_exp4$gender)
c(mean(participants_exp4$age), sd(participants_exp4$age)) %>% round(2)
```

## Figure 5

```{r Figure 5}

p_sp05 <- df2_exp4 %>%
  filter(restk == .5) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = .5, linetype = 2) +
  ggtitle(expression("Fixed speed = 0.5"*degree*"/s"))

p_sp1 <- df2_exp4 %>%
  filter(restk == 1) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 1, linetype = 2) +
  ggtitle(expression("Fixed speed = 1"*degree*"/s"))

p_sp2 <- df2_exp4 %>%
  filter(restk == 2) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 2, linetype = 2) +
  ggtitle(expression("Fixed speed = 2"*degree*"/s"))

p_sp4 <- df2_exp4 %>%
  filter(restk == 4) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 4, linetype = 2) +
  ggtitle(expression("Fixed speed = 4"*degree*"/s"))

p_sp8 <- df2_exp4 %>%
  filter(restk == 8) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 8, linetype = 2) +
  ggtitle(expression("Fixed speed = 8"*degree*"/s"))

p_sp8_legend <- df2_exp4 %>%
  filter(restk == 8) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 8, linetype = 2) +
  ggtitle(expression("Fixed speed = 8"*degree*"/s"))

gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 5)
ggsave("plots/Fig5_sp05.eps", p_sp05, width = 6, height = 6)
ggsave("plots/Fig5_sp1.eps", p_sp1, width = 6, height = 6)
ggsave("plots/Fig5_sp2.eps", p_sp2, width = 6, height = 6)
ggsave("plots/Fig5_sp4.eps", p_sp4, width = 6, height = 6)
ggsave("plots/Fig5_sp8.eps", p_sp8, width = 6, height = 6)
ggsave("plots/Fig5_sp8_legend.eps", p_sp8_legend, width = 6, height = 6)
# final plot was created in inkscape
```

## Compute the asymmetry

```{r compute the assymetry, warning=F}
df3_exp4 <- df2_exp4 %>% group_by(type, restk) %>% do(p=compute.p(.))

df3_exp4$p <- unlist(df3_exp4$p) %>% round(3)
df4_exp4 <- df2_exp4 %>% group_by(type, restk) %>% do(ges=compute.des(.))
df4_exp4$ges <- unlist(df4_exp4$ges) %>% round(2)
df3_exp4$ges <- df4_exp4$ges

df5_exp4 <- df2_exp4 %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
  group_by(type, restk) %>%
  summarize(acc_diff = accuracy[version == "fix distractors' speed"] - accuracy[version == "fix target's speed"])

m <- matrix(df3_exp4$ges, nrow = 5)
rownames(m) <- levels(df_exp4$type)
colnames(m) <- levels(df_exp4$type)
m[upper.tri(m,diag = T)] <- NA

df3_exp4$ges <- as.vector(m)

m <- matrix(df3_exp4$p, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp4$p <- as.vector(m)

m <- matrix(df5_exp4$acc_diff, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp4$acc_diff <- as.vector(m)

df3_exp4$target_lower_than_dist <- df3_exp4$acc_diff < 0
df3_exp4 %>% filter(target_lower_than_dist)

df3_exp4 %>% filter(p < 0.05)

differencies <- df3_exp4 %>% filter(target_lower_than_dist)  %>% .$acc_diff *-1
differencies %>% range() %>% round(2)

```

### 2018-01-03 R/exp1/01-parsedata.R

@@ -1,0 +1,11 @@
+rm(list = ls())
+
+pth <- "../data/exp1/responses/"
+
+files <- list.files(pth, pattern = "*.csv", full.names = T)
+
+df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
+
+str(df)
+
+save(df,file = "../data/exp1/responses/responses_150330.RData")

### 2018-01-03 R/exp2/01-parsedata.R

@@ -1,0 +1,11 @@
+rm(list = ls())
+
+pth <- "../data/exp2/responses/"
+
+files <- list.files(pth, pattern = "*.csv", full.names = T)
+
+df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
+
+str(df)
+df <- filter(df, subject != 1)
+save(df,file = "../data/exp2/responses/responses_150622.RData")

### 2018-01-03 R/exp2/create-protocols.R

@@ -1,0 +1,33 @@
+rm(list = ls())
+
+masterseed <- 198765
+
+create.protocol <- function(pid) {
+  set.seed(masterseed + pid)
+  n <- 202
+  p <- data.frame(pid = rep(pid, n),
+                  block = c(0,0,rep(1:4, each = (n - 2) / 4)),
+                  trial = 1:n,
+                  file = character(n),
+                  trialid = numeric(n),
+                  trialType = numeric(n),                  
+                  rest_k = numeric(n),
+                  stringsAsFactors = F)
+  ks <- c(2, 4, 8, 16, 64)
+  stopifnot((n - 2) %% length(ks) == 0)
+  
+  dfx <- rbind(expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks)) 
+  dfx <- dfx[sample(1:nrow(dfx)),]
+  
+  p$trialType <- c(sample(ks,2), dfx[,1]) 
+  p$trialid   <- sample(n) 
+  p$rest_k   <- c(sample(ks,2), dfx[,2])
+  p$file      <- sprintf("../trajectories/T%03d_%d_rest%d.csv", p$trialid, p$trialType, p$rest_k)
+    
+  return(p)
+}
+
+for (i in 1:100) {
+  p <- create.protocol(i)
+  write.csv(p,sprintf("../data/exp2/protocols/P%03d.csv", i), row.names = F)
+}

### 2018-01-03 R/exp3/01-parsedata.R

@@ -1,0 +1,14 @@
+rm(list = ls())
+
+pth <- "../data/exp3/responses/"
+
+files <- list.files(pth, pattern = "*.csv", full.names = T)
+
+df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
+
+df$restk <- as.numeric(gsub(".*rest(.*)\\.csv","\\1",df$file))
+df$type  <- as.numeric(gsub(".*_(.*)_rest.*","\\1",df$file))
+
+str(df)
+
+save(df,file = "../data/exp3/responses/responses_150410.RData")

### 2018-01-03 R/exp3/create-protocols.R

@@ -1,0 +1,29 @@
+rm(list = ls())
+
+masterseed <- 18766
+
+create.protocol <- function(pid) {
+  set.seed(masterseed + pid)
+  n <- 198
+  p <- data.frame(pid = rep(pid, n),
+                  block = c(0,0,rep(1:4, each = (n - 2) / 4)),
+                  trial = 1:n,
+                  file = character(n),
+                  trialid = numeric(n),
+                  trialType = numeric(n),                  
+                  rest_k = numeric(n),
+                  stringsAsFactors = F)
+  ks <- c(0.005, 0.01, 0.02, 0.03, 0.04, 0.06, 0.08)
+  stopifnot((n - 2) %% length(ks) == 0)
+  p$trialType <- c(sample(ks,2), sample(rep(ks, each = (n - 2) / length(ks)))) 
+  p$trialid   <- sample(n) 
+  p$rest_k   <- c(0.02,0.04,sample(c(rep(0.02,(n - 2) / 2), rep(0.04, (n - 2) / 2))))
+  p$file      <- sprintf("../trajectories/T%03d_%.03f_rest%.03f.csv", p$trialid, p$trialType, p$rest_k)
+    
+  return(p)
+}
+
+for (i in 1:100) {
+  p <- create.protocol(i)
+  write.csv(p,sprintf("../data/exp3/protocols/P%03d.csv", i), row.names = F)
+}

### 2018-01-03 R/exp4/01-parsedata.R

@@ -1,0 +1,11 @@
+rm(list = ls())
+
+pth <- "../data/exp4/responses/"
+
+files <- list.files(pth, pattern = "*.csv", full.names = T)
+
+df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
+
+str(df)
+
+save(df,file = "../data/exp4/responses/responses_171023.RData")

### 2018-01-03 R/tools.R

@@ -1,0 +1,69 @@
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  # source: http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)/
+  library(grid)
+  
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+  
+  numPlots = length(plots)
+  
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                     ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+  
+  if (numPlots==1) {
+    print(plots[[1]])
+    
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+    
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+      
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+
+
+thresh.est <- function(p1 = 0.6, model) {
+  q.5   <- -coef(model)[1] / coef(model)[2]
+  sigma <- 1/coef(model)[2]
+  th <- exp(qnorm(p = p1,
+                  mean = q.5, sd = sigma))
+  return(th)
+}
+
+compute.p <- function(dfx) {
+  aov1 <- ezANOVA(as.data.frame(dfx),
+                  dv = accuracy,
+                  wid = subject,
+                  within = version)
+  return(aov1$ANOVA$p)
+}
+compute.ges <- function(dfx) {
+  aov1 <- ezANOVA(as.data.frame(dfx),
+                  dv = accuracy,
+                  wid = subject,
+                  within = version)
+  return(aov1$ANOVA$ges)
+}
+
+compute.des <- function(dfx) {
+  means <- ezStats(as.data.frame(dfx),
+                   dv = accuracy,
+                   wid = subject,
+                   within = version)
+  return(diff(means$Mean))
+  
+}

### 2018-01-03 matlab/GetProtocolInfo.m

@@ -1,0 +1,45 @@
+function info = GetProtocolInfo(protocol)
+%GetProtocolInfo - Gets information from protocol
+% Gets information from cell array and stores them in struct. This is an
+% utility function for better readibility of code (cell arrays aren't self
+% explaining.
+%   
+% Syntax:  GetProtocolInfo(protocol)
+%
+% Inputs:
+%    protocol - cell array with raw protocol data
+%
+% Outputs:
+%    info - struct with informations about protocol
+%
+% Example:
+%    protocolPath='protocols/P001.csv';    
+%    protocol=LoadProtocol(protocolPath);
+%    pinfo=GetProtocolInfo(protocol);
+%    fprintf('Protocol loaded, there are %d trials in this experiment,pinfo.ntrials);
+%
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also: LoadProtocol,GetProtocolInfo
+
+% Author: Filip Dechterenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Apr 2011; Last revision: 26.06.2012
+
+%------------- BEGIN CODE --------------
+    info = {};
+    info.pid     = protocol{1}'; % integers
+    info.block   = protocol{2}'; % integers
+    info.trial   = protocol{3}';  % integers
+    info.file    = protocol{4}';  % integers
+    info.trackid = protocol{5}';  % cell
+    info.type    = protocol{6}'; % integers
+    info.ntrials = length(info.trial); % single int
+    info.blocks = unique(info.block);  % vector of unique integers
+    info.nblocks = length(info.blocks); % single int
+%------------- END OF CODE --------------
+end

### 2018-01-03 matlab/LoadProtocol.m

@@ -1,0 +1,52 @@
+function protocol = LoadProtocol(dataFileName, protStringPattern, headerLines)
+%LoadProtocol - Loads protocol from specified data file
+%Loads protocol for experiment from file.
+%
+% Syntax:  protocol = LoadProtocol(dataFileName)
+%
+% Inputs:
+%    dataFileName - path to the protocol file (usualy stored as .csv)
+%
+% Outputs:
+%    protocol - cell array with protocol
+%
+% Example:
+%    protocol = LoadProtocol('../data/protocols/P001.csv')
+%
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also: GenerateProtocols
+
+% Author: Filip Dechterenko 
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Apr 2011; Last revision: 26.06.2012
+
+%------------- BEGIN CODE --------------
+
+if (~exist(dataFileName,'file'))
+    error('crowdMOT:technicalProblems','File with protocol "%s" doesn''t exist\n',dataFileName);
+end
+
+if(nargin < 2), 
+    conf = getExperimentInfo();
+    protStringPattern = conf.protStringPattern;
+end
+
+if(nargin < 3), headerLines = 1; end
+
+dataFile = fopen(dataFileName, 'r');
+protocol = textscan(dataFile, protStringPattern, 'Delimiter', ',',...
+    'Headerlines',headerLines);
+
+fclose(dataFile);
+if (numel(protocol{end})==0)
+    warning('crowdMOT:technicalProblems','protocol file "%s" doesn''t contain any data (probably is badly formated). Data should be delimited by comma.\n',dataFileName);
+end
+fprintf('Protocol file "%s" successfully loaded\n',dataFileName);
+
+%------------- END OF CODE --------------
+end

### 2018-01-03 matlab/StartExperiment.m

@@ -1,0 +1,594 @@
+function StartExperiment(identifier)
+% StartExperiment - Main procedure for administrating experiment.
+% In prior to successful testing, all protocols and trajectories have to be
+% generated. Needs PsychToolBox-3 to run.
+%
+% Syntax: StartExperiment()
+%
+% Example:
+%    % we need trajectories and protocols generated in files specified in experiment info
+%    % configuration file
+%    StartExperiment()
+%
+% Other m-files required: GetExperimentInfo.m, PixelSize.m, LoadProtocol.m, GetProtocolInfo.m, LoadTrajectories.m, WaitMouse.m
+% Subfunctions: cleanup
+% MAT-files required: none
+%
+% See also:  StartExperiment
+%
+% Author: Filip Dechtìrenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Mar 2012; Last revision: 26.06.2012
+
+%------------- BEGIN CODE --------------
+    function cleanup
+    % simple function for shutting down eyelink and closing window
+    if eEyelink, Eyelink('Shutdown'); end
+    sca;
+    commandwindow;
+    end
+
+%% ----------------------------------------------------------
+% Set variables about experiment
+% -----------------------------------------------------------
+
+confFilePath = './sharedfunctions';
+addpath(confFilePath);
+expInfo = GetExperimentInfo(confFilePath);
+
+protDir = expInfo.protDir;
+if (~exist(protDir,'dir'))
+    error('vonMissesMot01:technicalProblems', 'Directory with protocols don''t exist!');
+end
+
+
+trajDir = expInfo.trajDir;
+if (~exist(trajDir,'dir'))
+    error('vonMissesMot01:technicalProblems', 'Directory with trajectories don''t exist!');
+end
+
+resultsDir = expInfo.outDir;
+if (~exist(resultsDir,'dir'))
+    error('vonMissesMot01:technicalProblems', 'Output directory don''t exist!');
+end
+
+%eyeDir = expInfo.eyeDir;
+%if (~exist(eyeDir,'dir'))
+%    error('vonMissesMot01:technicalProblems','Directory for eye data don''t exist!');
+%end
+
+
+% default values for testing
+if (nargin<1), identifier = 0; end
+
+protocolName = sprintf('P%03d', identifier);
+
+clear Screen; % to ensure clean run
+
+% set random generator
+RandStream.setGlobalStream(RandStream('mt19937ar', 'seed', 500 + identifier))
[…]

### 2018-01-03 matlab/generate_data/CreateProtocols.m

@@ -1,0 +1,108 @@
+function CreateProtocols(expInfo)
+%CreateProtocols - Creates protocols for experiment.
+%Creates protocols for experiments. Each protocol contains list of trials which
+%will be presented to participant. Must be run after trajectories are
+%created
+%
+% Syntax: CreateProtocols(expInfo)
+%         
+% Inputs:
+%   expInfo          - struct with experiment configuration
+%
+% Example:
+%   expInfo=GetExperimentInfo('../shared functions');
+%   
+%   CreateProtocols(expInfo)
+%
+%
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also:  CreateTrajectories
+%
+% Author: Filip Dechterenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Apr 2011; Last revision: 17.02.2013
+
+%------------- BEGIN CODE --------------
+
+% script for generating protocols from trajectories
+% in this experiment, we have only 4+4 configuration
+% in each block, we have 5 LR trials and 5 unique, we have 6 blocks, so 90
+% trials in total
+% 5 trial will be used for training
+
+outDir=fullfile('..',expInfo.protDir);
+if (~exist(outDir,'dir'))
+    sprintf('Info: outDir %s dont exists, creating',outDir);
+    mkdir(outDir);
+end
+
+nProtocols=expInfo.protocols;
+
+nTargets=expInfo.targets;
+nBlockCount = expInfo.blocks;
+nTrialsInBlock = expInfo.trials;
+nTrialsTraining=expInfo.nTrialsTraining;
+
+nTrials=nBlockCount*nTrialsInBlock+nTrialsTraining;
+
+nTraj=expInfo.traj;
+nRepTraj=expInfo.repInBlock;
+nRandom=expInfo.ranInBlock;
+
+% "block","trial","type","trackid","file","trackfirst","trialStart"
+for ix=1:nProtocols % for each protocol
+    fileName=fullfile(outDir,sprintf('P%03d.csv',ix));
+    protFile = fopen(fileName, 'w');
+    fprintf(protFile,'block,trial,type,trackid,file,trackfirst,trialStart\n');
+    
+    % select repeating trials
+    trialPermutation=randperm(nTraj);
[…]

### 2018-01-03 matlab/generate_data/CreateTrajectories_exp1.m

@@ -1,0 +1,103 @@
+am function CreateTrajectories_exp1(expInfo)
+%CreateTrajectories - generate files with trajectories
+%
+% Syntax: GenerateRandomTrajectories(count,nPoints,nFrames,positionGrid,pixelsPerFrame,objectPixels,fieldRect)
+%
+% Inputs:
+%   expInfo            - struct with experiment parameters
+%
+% Example:
+%   confFilePath='./sharedfunctions';
+%   expInfo=GetExperimentInfo(confFilePath);
+%   CreateTrajectories(expInfo)
+%
+% Other m-files required: SubsetPositions.m, GenerateTrajectories.m
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also:  CreateTrajectories,GenerateTrajectories
+%
+% Author: Filip Dechterenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Apr 2011; Last revision: 09.10.2012
+
+%------------- BEGIN CODE --------------
+
+if(nargin<1)
+    confFilePath='../sharedfunctions';
+    addpath(confFilePath);
+    expInfo = GetExperimentInfo(confFilePath);
+end
+
+outputdir = fullfile('..',expInfo.trajDir); % output directory for trajectories
+if (~exist(outputdir, 'dir'))
+    fprintf('Info: outputdir %s dont exists, creating',outputdir);
+    mkdir(outputdir);
+end
+
+RandStream.setGlobalStream(RandStream('mt19937ar', 'seed', 12345))
+
+nTargets     = expInfo.targets;
+nDistractors = expInfo.distractors;
+
+
+startingGrid = [expInfo.gridSize, expInfo.gridSize];
+if (expInfo.gridSize^2 < nDistractors+nTargets)
+    error('Incorrectly set parameters: max capacity of the grid is lower then max number of points');
+end
+
+
+% create starting grid
+positionsGrid = StartingPositionsGrid(startingGrid, [0,0], ...
+    [expInfo.startWidth, expInfo.startHeigth] ./ (startingGrid - [1,1]));
+
+
+nDots = nTargets + nDistractors;
+trackInfo = struct(...
+    'nDots', nDots, ...
+    'k', repmat(16, nDots,1), ...
+    'degSize', repmat(0.02, nDots,1), ...
+    'nFrames', 800, ... % 8 seconds of movement
[…]

### 2018-01-03 matlab/generate_data/CreateTrajectories_exp2.m

@@ -1,0 +1,107 @@
+function CreateTrajectories_exp2(expInfo)
+%CreateTrajectories - generate files with trajectories
+%
+% Syntax: GenerateRandomTrajectories(count,nPoints,nFrames,positionGrid,pixelsPerFrame,objectPixels,fieldRect)
+%
+% Inputs:
+%   expInfo            - struct with experiment parameters
+%
+% Example:
+%   confFilePath='./sharedfunctions';
+%   expInfo=GetExperimentInfo(confFilePath);
+%   CreateTrajectories(expInfo)
+%
+% Other m-files required: SubsetPositions.m, GenerateTrajectories.m
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also:  CreateTrajectories,GenerateTrajectories
+%
+% Author: Filip Dechterenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Apr 2011; Last revision: 09.10.2012
+
+%------------- BEGIN CODE --------------
+
+if(nargin<1)
+    confFilePath='../sharedfunctions';
+    addpath(confFilePath);
+    expInfo = GetExperimentInfo(confFilePath);
+end
+
+% outputdir = fullfile('..',expInfo.trajDir); % output directory for trajectories
+outputdir = '../data/exp2/trajectories';
+if (~exist(outputdir, 'dir'))
+    fprintf('Info: outputdir %s dont exists, creating',outputdir);
+    mkdir(outputdir);
+end
+
+RandStream.setGlobalStream(RandStream('mt19937ar', 'seed', 112345))
+
+nTargets     = expInfo.targets;
+nDistractors = expInfo.distractors;
+
+startingGrid = [expInfo.gridSize, expInfo.gridSize];
+if (expInfo.gridSize^2 < nDistractors+nTargets)
+    error('Incorrectly set parameters: max capacity of the grid is lower then max number of points');
+end
+
+% create starting grid
+positionsGrid = StartingPositionsGrid(startingGrid, [0,0], ...
+    [expInfo.startWidth, expInfo.startHeigth] ./ (startingGrid - [1,1]));
+
+nDots = nTargets + nDistractors;
+trackInfo = struct(...
+    'nDots', nDots, ...
+    'k', repmat(16, nDots,1), ...
+    'degSize', repmat(0.02, nDots,1), ...
+    'nFrames', 800, ... % 8 seconds of movement
[…]

### 2018-01-03 matlab/generate_data/CreateTrajectories_exp3.m

@@ -1,0 +1,110 @@
+function CreateTrajectories_exp3(expInfo)
+%CreateTrajectories - generate files with trajectories
+%
+% Syntax: GenerateRandomTrajectories(count,nPoints,nFrames,positionGrid,pixelsPerFrame,objectPixels,fieldRect)
+%
+% Inputs:
+%   expInfo            - struct with experiment parameters
+%
+% Example:
+%   confFilePath='./sharedfunctions';
+%   expInfo=GetExperimentInfo(confFilePath);
+%   CreateTrajectories(expInfo)
+%
+% Other m-files required: SubsetPositions.m, GenerateTrajectories.m
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also:  CreateTrajectories,GenerateTrajectories
+%
+% Author: Filip Dechterenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Apr 2011; Last revision: 09.10.2012
+
+%------------- BEGIN CODE --------------
+
+if(nargin<1)
+    confFilePath='../sharedfunctions';
+    addpath(confFilePath);
+    expInfo = GetExperimentInfo(confFilePath);
+end
+expInfo.trajDir = '../data/exp3/trajectories';
+outputdir = fullfile('..',expInfo.trajDir); % output directory for trajectories
+if (~exist(outputdir, 'dir'))
+    fprintf('Info: outputdir %s dont exists, creating',outputdir);
+    mkdir(outputdir);
+end
+
+RandStream.setGlobalStream(RandStream('mt19937ar', 'seed', 12345))
+
+nTargets     = expInfo.targets;
+nDistractors = expInfo.distractors;
+
+startingGrid = [expInfo.gridSize, expInfo.gridSize];
+if (expInfo.gridSize^2 < nDistractors+nTargets)
+    error('Incorrectly set parameters: max capacity of the grid is lower then max number of points');
+end
+
+% create starting grid
+positionsGrid = StartingPositionsGrid(startingGrid, [0,0], ...
+    [expInfo.startWidth, expInfo.startHeigth] ./ (startingGrid - [1,1]));
+
+
+
+
+nDots = nTargets + nDistractors;
+trackInfo = struct(...
+    'nDots', nDots, ...
+    'k', repmat(16, nDots,1), ...
[…]

### 2018-01-03 matlab/generate_data/CreateTrajectories_exp4.m

@@ -1,0 +1,98 @@
+function CreateTrajectories_exp4(expInfo)
+%CreateTrajectories - generate files with trajectories
+%
+% Syntax: GenerateRandomTrajectories(count,nPoints,nFrames,positionGrid,pixelsPerFrame,objectPixels,fieldRect)
+%
+% Inputs:
+%   expInfo            - struct with experiment parameters
+%
+% Example:
+%   confFilePath='./sharedfunctions';
+%   expInfo=GetExperimentInfo(confFilePath);
+%   CreateTrajectories(expInfo)
+%
+% Other m-files required: SubsetPositions.m, GenerateTrajectories.m
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also:  CreateTrajectories,GenerateTrajectories
+%
+% Author: Filip Dechterenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Apr 2011; Last revision: 09.10.2012
+
+%------------- BEGIN CODE --------------
+
+if(nargin<1)
+    confFilePath='../sharedfunctions';
+    addpath(confFilePath);
+    expInfo = GetExperimentInfo(confFilePath);
+end
+
+% outputdir = fullfile('..',expInfo.trajDir); % output directory for trajectories
+outputdir = '../data/exp4/trajectories';
+if (~exist(outputdir, 'dir'))
+    fprintf('Info: outputdir %s dont exists, creating',outputdir);
+    mkdir(outputdir);
+end
+
+RandStream.setGlobalStream(RandStream('mt19937ar', 'seed', 112345))
+
+nTargets     = expInfo.targets;
+nDistractors = expInfo.distractors;
+
+%if size(distLevels,2)~=nDiff, error('crowdMOT:technicalProblems','Incorrectly set parameters - '), end
+
+% set fps for experiment
+% we'll generate trajectories for 100 fps and then interpolate for each
+% monitor just before presentation
+%fps= 100;
+
+startingGrid = [expInfo.gridSize, expInfo.gridSize];
+if (expInfo.gridSize^2 < nDistractors+nTargets)
+    error('Incorrectly set parameters: max capacity of the grid is lower then max number of points');
+end
+
+
+% create starting grid
+positionsGrid = StartingPositionsGrid(startingGrid, [0,0], ...
[…]

### 2018-01-03 matlab/generate_data/GenerateTrajectoryVonMises.m

@@ -1,0 +1,103 @@
+function trajectory = GenerateTrajectoryVonMises(trackInfo, startPositions)
+% GenerateTrajectoryVonMises - generates trajectory sampling from von mises distribution
+
+if (nargin<1)
+    nDots   = 8;
+    k       = repmat(16, nDots,1); % ballistic-like-distractors
+    degSize = repmat(0.02, nDots,1);
+    nFrames = 600;
+    a       = 15;
+    speedVarCoef    = repmat(0.01, nDots, 1); %0.1;
+    changeVarCoef   = 0.1;
+    meanChangeFrame = 8;    
+else
+    nDots   = trackInfo.nDots;
+    k       = trackInfo.k;
+    degSize = trackInfo.degSize;
+    nFrames = trackInfo.nFrames;
+    a       = trackInfo.arenaEdge/2;
+    speedVarCoef    = repmat(trackInfo.speedVarCoef, nDots, 1);
+    changeVarCoef   = trackInfo.changeVarCoef;
+    meanChangeFrame = trackInfo.meanChangeFrame;
+end
+
+    
+fieldRect           = [-a, -a, a, a]; % rectangle, where will dot move
+
+objectPixels        = 1;
+interItemBufferZone = objectPixels * 1.10;
+
+% define borders
+leftEdge   = fieldRect(RectLeft) + objectPixels;
+rightEdge  = fieldRect(RectRight) - objectPixels;
+topEdge    = fieldRect(RectTop) + objectPixels;
+bottomEdge = fieldRect(RectBottom) - objectPixels;
+
+% initialize directions
+oldCoordinates  = startPositions; %-(a - 1) + (2 * (a - 1)) .* rand(2, nDots);
+theta           = rand(1, nDots) * 2 * pi;
+
+trajectory      = zeros(2, nDots, nFrames);
+newCoordinates  = oldCoordinates;
+thetaDeltas    = zeros(nFrames, nDots);
+
+% pre-generate all trajectory changes
+for i=1:nDots
+    thetaDeltas(:,i) = randraw('vonmises', [0, k(i)], nFrames, 1);
+end
+
+% pre-generate all speed changes
+speeds          = repmat(degSize, 1, nFrames + 1)' + (repmat(speedVarCoef', nFrames + 1,1) .* repmat(degSize, 1, nFrames + 1)') .* randn(nFrames + 1, nDots);
+
+% set the frames, where will the speed and angle change
[…]

### 2018-01-03 matlab/generate_data/JitterPositions.m

@@ -1,0 +1,16 @@
+function newPositions = JitterPositions(positions, jitterRadiusPixels)
+% function newPositions = JitterPositions(positions, jitterRadiusPixels)
+%
+% Jitters point positions using uniform random jitter with a specified
+% radius 
+%
+%   positions          = (2, nPoints) original positions
+%   jitterRadiusPixels = (jx, jy) radius in pixels, maximum jitter size
+%
+% Returns (2, nPoints) vector with new positions
+
+    %nPoints = size(positions, 2)
+    randomJitter = rand(size(positions)) - .5;
+    noise = diag(jitterRadiusPixels) * randomJitter;
+    newPositions = noise + positions;
+end

### 2018-01-03 matlab/generate_data/StartingPositionsGrid.m

@@ -1,0 +1,58 @@
+function positions = StartingPositionsGrid(nPoints, centerPixels, distancePixels)
+%StartingPositionsGrid - Generates grid with positions.
+%Generates starting grid with positions where can be objects located in
+%beginning of the trial. Those positions are centered around central point
+%and have fixed distance between them
+%
+% Syntax: positions = StartingPositionsGrid(nPoints, centerPixels, distancePixels)
+%         
+% Inputs:
+%   nPoints        - vector in format [nx,ny], where nx/ny is number of points in row/column
+%   centerPixels   - vector in format [x,y], where x,y are coordinates of the center
+%   distancePixels - vector in format [sx, sy], where sx/sy is distance between objects in row/column
+%
+% Outputs:
+%   positions - (2 x n) array with positions, where n=nx*ny
+%
+% Example:
+%   expInfo=GetExperimentInfo('../sharedfunctions');
+%   startingGrid = [expInfo.gridSize, expInfo.gridSize];
+%   positionsGrid = StartingPositionsGrid(startingGrid, [0,0], ...
+%        [expInfo.startWidth, expInfo.startHeigth] ./ (startingGrid - [1,1]));
+%
+%
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also:  SubsetPositions
+%
+% Author: Filip Dechterenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Apr 2011; Last revision: 26.06.2012
+
+%------------- BEGIN CODE --------------
+
+% if we called grid generation with only one number for nPoints, we'll
+% consider it as square
+if size(nPoints, 2) == 1
+    nPoints = [nPoints nPoints];
+end
+
+% same with distance
+if size(distancePixels, 2) == 1
+    distancePixels = [distancePixels distancePixels];
+end
+nPositions = nPoints(1) * nPoints(2);
+positions = zeros(2, nPositions);
+[xpos, ypos] = meshgrid(1:nPoints(1),1:nPoints(2));
+xpos = xpos(:) - (nPoints(1) - 1) / 2 - 1;  % center them first
+ypos = ypos(:) - (nPoints(1) - 1) / 2 - 1;  % -1 because they start with 1 not 0
+% scale them
+positions(1, :) = centerPixels(1) + xpos * distancePixels(1);
[…]

### 2018-01-03 matlab/generate_data/SubsetPositions.m

@@ -1,0 +1,53 @@
+function newPositions = SubsetPositions(nSelect, positions, random)
+%SubsetPositions - select several points from position grid
+%Select several positions from grid. Data can be selected randmly or we
+%could take first several points
+%
+% Syntax: newpositions = SubsetPositions(nSelect, positions, random)
+%         
+% Inputs:
+%   nSelect        - either number of points to select, or vector of indexes
+%   positions      - (2, nPoints) array with positions
+%   random         - 1 if points should be selected randomly, 0 if we just
+%   take first nPoints positions
+%
+% Outputs:
+%   newPositions - (2 x nSelect) array with positions
+%
+% Example:
+%   % we will generate starting grid somehow (e.g. with StartingPositionsGrid
+%   positions = SubsetPositions(nPoints, positionGrid, 1);   
+%
+% Remarks:
+%    Works also for trajectories: accepts (2, nP, nFr) as positions and
+%    returns (2, nSelect, nFr) matrix.
+% 
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also:  StartingPositionsGrid
+%
+% Author: Filip Dechterenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Apr 2011; Last revision: 26.06.2012
+
+%------------- BEGIN CODE --------------
+
+nPoints = size(positions, 2);
+if size(nSelect, 2) == 1
+    index = 1:nSelect;  % if (int) n is provided, we take first n
+else
+    index = nSelect;
+end
+
+if random == 1
+    positions = positions(:,randperm(nPoints),:);
+end
+
+newPositions = positions(:,index,:);
+
+%------------- END OF CODE --------------
+end

### 2018-01-03 matlab/generate_data/computeCoordinates.m

@@ -1,0 +1,18 @@
+function newCoordinates = computeCoordinates(oldCoordinates, theta, magnitude)
+%computeCoordinates - computes new coordinates using polar system.
+%
+% Syntax:
+%   newCoordinates - computeCoordinates(oldCoordinates, theta, magnitude)
+%         
+% Inputs:
+%   oldCoordinates - (2,nPoints) array with current coordinates for dots
+%   theta          -  direction change
+%   magnitude      - magnitude of coordinate change
+%
+% Outputs:
+%   newCoordinates - (2,nPoints) array with new coordinates for dots
+
+newCoordinates(1, :) = magnitude .* sin(theta) + oldCoordinates(1, :); %x coordinate of the next point
+newCoordinates(2, :) = magnitude .* cos(theta) + oldCoordinates(2, :); %y coordinate of the next point
+
+end

### 2018-01-03 matlab/sharedfunctions/Contents.m

@@ -1,0 +1,25 @@
+% CrowdMOT Experiment - shared functions
+% Functions which are used in experiment part
+% Author: Filip Dechterenko
+% Version: 1.0
+% Date: 04.07.2012
+%
+% ------------------------------------------------------------------------
+%
+% Configuration is stored in file expInfo.txt, some values can be set in 
+% functions manually.  
+%
+% ------------------------------------------------------------------------
+%
+% Utility functions:
+% GetExperimentInfo - Loads information from experiment info struct and
+% returns them as struct. If experiment info is missing, default one will
+% be created
+% LoadResponse - Loads response from experiment for participant
+% LoadTrajectories - Loads trajectories from file
+% PixelSize - Computes size of degree in pixels
+% PressToContinue - Waits for specified key to be pressed
+
+
+
+

### 2018-01-03 matlab/sharedfunctions/GetExperimentInfo.m

@@ -1,0 +1,155 @@
+function expinfo = GetExperimentInfo(path)
+% GetExperimentInfo - Loads experiment info file. If this file is missing,
+% creates default one.
+% Shared configuration is stored in expInfo file, configuration is loaded
+% dynamicaly, so it's easy to add new option.
+%
+% Syntax: GetExperimentInfo(path)
+%         GetExperimentInfo()
+% Inputs:
+%    path - path to experiment info file or dir, where is experiment info
+%    file located
+%         
+% Example:
+%    path='./sharedfunctions';
+%    expInfo=GetExperimentInfo(path);
+%
+% Other m-files required: none
+% Subfunctions: CreateExperimentInfo
+% MAT-files required: none
+%
+% See also:  StartExperiment
+%
+% Author: Filip Dechterenko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% May 2011; Last revision: 26.06.2012
+
+%------------- BEGIN CODE --------------
+
+if (nargin<1)
+    % use default file
+    path='expinfo.txt';
+end
+% if we are calling this function with directory as path, we add
+% expinfo.txt to the end
+if (isempty(regexp(path,'.*expinfo.txt$', 'once')))
+    path=fullfile(path,'expinfo.txt');
+end
+if (~exist(path,'file'))
+    fprintf(sprintf('Expinfo file "%s" doesn''t exists, creating new one with default parameters',path));
+    CreateExperimentInfo(path);
+end
+
+f = fopen(path,'r');
+expinfodata = textscan(f,'%s%s','Delimiter','=',...
+    'CommentStyle','#');
+fclose(f);
+
+% we load data dynamicaly, new options can be added easily in format
+% option=value
+expinfo=struct();
+for ikey=1:size(expinfodata{1},1)
+    val=expinfodata{2}{ikey};
+    [vali,status]=str2num(val); %#ok<ST2NM>
+    if (status==1)
+        val=vali;
+    end
+    expinfo.(expinfodata{1}{ikey})=val;
+end
+
+fprintf('expInfo file successfully loaded.\n')
+
+%------------- END OF CODE --------------
+end
+
+function CreateExperimentInfo(file)
+% creates default experiment info file.
+fileptr = fopen(file,'w');
[…]

### 2018-01-03 matlab/sharedfunctions/LoadResponse.m

@@ -1,0 +1,49 @@
+function [speed,response] = LoadResponse(fileName)
+%LoadResponse - Loads participant response from file
+%Loads participant response from file.
+%
+% Syntax: [speedPerSec,response] = LoadResponse(fileName)
+%
+% Inputs:
+%    rawdata    - raw eye data from parseasc utility
+%    response   - struct with subject responses
+%
+% Outputs:
+%    speed      - speed with which dots moved
+%    response   - cell array with response information
+%
+% Example:
+%    responseFile='../../data/responses/data-04.csv';
+%    [speedPerSec,response]=LoadResponse(responseFile);
+%
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also: ParseData
+%
+% Author: Filip Dechterenko 
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Mar 2012; Last revision: 30.06.2012
+
+%------------- BEGIN CODE --------------
+
+% gets speed and response from file
+dataFile = fopen(fileName, 'r');
+response=textscan(dataFile,'%d%d%d%q%q%d%d%f%d','Delimiter',',',...
+    'Headerlines',3);
+
+% response loaded, now get speed
+frewind(dataFile);
+fgetl(dataFile);fgetl(dataFile);
+speedStr=fgetl(dataFile);
+ix=strfind(speedStr,':');
+speedStr(1:ix)=[];
+speed=str2double(speedStr);
+fclose(dataFile);
+
+%------------- END OF CODE -------------- 
+
+end

### 2018-01-03 matlab/sharedfunctions/LoadTrajectories.m

@@ -1,0 +1,58 @@
+function [data,comment] = LoadTrajectories(dataFileName)
+%LoadTrajectories - Loads trajectories from specified data file
+%Loads trajectories from file
+%
+% Syntax:  [data,comment] = LoadTrajectories(dataFileName)
+%
+% Inputs:
+%    dataFileName - path to file containing trajectory
+%
+% Outputs:
+%    data         - (2,nPoints,nFrames) matrix with trajectory for experiment
+%    comment      - comment from header line of file
+%
+% Example:
+%    dataFile='../data/tracks/R001.csv';
+%    [data,comment]=LoadTrajectories(dataFile)
+%    fprintf('Trajectory from file %s loaded\nComment: %s\n',dataFile,comment);
+%
+%
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also: ExperimentDemo, StartExperiment
+%
+% Author: Filip Dechterenko 
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Feb 2012; Last revision: 01.07.2012
+
+%------------- BEGIN CODE --------------
+
+dataFile = fopen(dataFileName, 'r');
+
+comment = fgetl(dataFile) ;
+line1 = fgetl(dataFile);
+d1 = sscanf(line1,'%f');
+howmany1 = size(d1,1);
+frewind(dataFile);
+fgetl(dataFile);
+dataraw = fscanf(dataFile, '%f');
+dataraw = reshape(dataraw, howmany1, []);
+dataraw = dataraw';
+fclose(dataFile);
+
+% reshape trajectories
+xindex = 1:2:howmany1;  % odd numbers
+yindex = 2:2:howmany1;  % even
+nPoints = howmany1 / 2;
+nFrames = size(dataraw, 1);
+data = zeros(2, nPoints, nFrames);
+data(1,:,:) = dataraw(:,xindex)';
+data(2,:,:) = dataraw(:,yindex)';
+   
+%------------- END OF CODE -------------- 
+
+end

### 2018-01-03 matlab/sharedfunctions/PixelSize.m

@@ -1,0 +1,42 @@
+function pixSize = PixelSize(degSize,viewDistance,screenResolution,monitorSize)
+%PixelSize - Loads participant response from file
+%Loads participant response from file.
+%
+% Syntax: pixSize = PixelSize(degSize,viewDistance,screenResolution,monitorSize)
+%
+% Inputs:
+%   degSize          - size in degrees (1 or 2 dim)
+%   viewDistance     - viewing distance in cm
+%   screenResolution - resolution in pixels (1 or 2 dim)
+%   monitorSize      - screen size in cm (or same units as viewDistance)
+%
+% Outputs:
+%    pixSize         - size of degSize degrees in pixels
+%
+% Example:
+%    degSize=1;
+%    viewingDistance=50;
+%    screenResolution=1280;
+%    monitorSize=45.14;
+%    pixSize = PixelSize(degSize,viewingDistance,screenResolution,monitorSize);
+%
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also: ParseData
+%
+% Author: Filip Dechterenko 
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Mar 2012; Last revision: 30.06.2012
+
+%------------- BEGIN CODE --------------
+    radSize = degSize ./ 180 .* pi;
+    cmSize  = 2 .* viewDistance .* tan(radSize ./ 2);
+    pixSize = cmSize ./ monitorSize .* screenResolution;
+    
+%------------- END OF CODE -------------- 
+ 
+end

### 2018-01-03 matlab/sharedfunctions/PressToContinue.m

@@ -1,0 +1,66 @@
+function status = PressToContinue(keyName, quitKey)
+%PressToContinue -  Wait for a particular key to be pressed
+%If keyName is not provided, any key will do
+%
+% Syntax:  status = PressToContinue(keyName, quitKey)
+%
+% Inputs:
+%    keyName - key, which should be pressed
+%    quitKey - key to quit
+%
+% Outputs:
+%    status - Returns 0 for Escape, 1 otherwise
+%
+% Example:
+%    
+%
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also: 
+%
+% Author: Todd Horowitz
+% Modified: Filip Dìchtìrnko
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% May 2012; Last revision: 13.05.2012
+
+%------------- BEGIN CODE --------------
+
+if nargin >= 1 && ~isempty(keyName)
+    specificKey = KbName(keyName);
+    anyFlag = 0;
+else
+    anyFlag = 1;
+end
+
+if nargin == 2
+    escapeCode = KbName(quitKey);
+else
+    escapeCode = KbName('Escape');
+end
+
+sitFlag = 1;
+while sitFlag
+    [keyIsDown, ~, keyCode] = KbCheck;
+    if keyIsDown
+        response = find(keyCode);
+        response = response(1);
+        if anyFlag || response == specificKey
+            sitFlag = 0;
+            status = 1;
+        end
+
+        if response == escapeCode
+            sitFlag = 0;
+            status = 0;
+        end
+    end
+end
+% now wait for the key to come up again
+while KbCheck; end
+
+%------------- END OF CODE --------------
+end

### 2018-01-03 matlab/sharedfunctions/ResampleTrajectory.m

@@ -1,0 +1,50 @@
+function [resampledTraj] = ResampleTrajectory(expInfo,traj,fps)
+%ResampleTrajectory - Resamples trajectories to new fps
+%All trajectories are generated for 100 fps. We will use interpolation to
+%change speed for specified fps
+%
+% Syntax:  [resampledTraj] = ResampleTrajectory(traj,fps)
+%
+% Inputs:
+%    traj          - (2,nPoints,nFrames) matrix with trajectory for experiment
+%    fps           -  new fps
+%
+% Outputs:
+%    resampledTraj - (2,nPoints,nFrames) matrix with trajectory for experiment
+%
+% Example:
+%    traj=GenerateTrajectoryVonMises()
+%    resampledTraj=ResampleTrajectory(traj,60)
+%
+%
+% Other m-files required: none
+% Subfunctions: none
+% MAT-files required: none
+%
+% See also: GenerateTrajectory
+%
+% Author: Filip Dechterenko 
+% MFF UK
+% email: filip.dechterenko@gmail.com
+% Website: http://ms.mff.cuni.cz/~dechf7am
+% Feb 2012; Last revision: 07.01.2013
+
+%------------- BEGIN CODE --------------
+
+% Changes speed for generated trajectory 
+generatedFps=expInfo.generatedFps;
+nLength=numel(1:(generatedFps/fps):size(traj,3));
+resampledTraj=zeros(size(traj,1),size(traj,2),nLength);
+for jx=1:size(traj,2)        
+    for ix=1:2
+        a=traj(ix,jx,:); % maybe some simple solution with NDim matrixes
+        a=a(:)';
+        b=interp1(a,1:(generatedFps/fps):size(traj,3));
+        resampledTraj(ix,jx,:) = b;        
+    end
+end
+fprintf('Trajectory resampled to fps %f\n',fps);
+
+%------------- END OF CODE -------------- 
+
+end

### 2018-07-02 R/exp1/01-parsedata.R
rename experiments
also store the data as rds instead of rdata

@@ -1,11 +1,0 @@
-rm(list = ls())
-
-pth <- "../data/exp1/responses/"
-
-files <- list.files(pth, pattern = "*.csv", full.names = T)
-
-df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
-
-str(df)
-
-save(df,file = "../data/exp1/responses/responses_150330.RData")

### 2018-07-02 R/exp1/create-protocols.R

@@ -1,29 +1,0 @@
-rm(list = ls())
-
-masterseed <- 98765
-
-create.protocol <- function(pid) {
-  set.seed(masterseed + pid)
-  n <- 194
-  p <- data.frame(pid = rep(pid, n),
-                  block = c(0,0,rep(1:4, each = (n - 2) / 4)),
-                  trial = 1:n,
-                  file = character(n),
-                  trialid = numeric(n),
-                  trialType = numeric(n),                  
-                  rest_k = numeric(n),
-                  stringsAsFactors = F)
-  ks <- c(1, 2, 4, 8, 16, 32, 64, 128)
-  stopifnot((n - 2) %% length(ks) == 0)
-  p$trialType <- c(sample(ks,2), sample(rep(ks, each = (n - 2) / length(ks)))) 
-  p$trialid   <- sample(n) 
-  p$rest_k   <- c(4,64,sample(c(rep(4,(n - 2) / 3), rep(16, (n - 2) / 3), rep(64,(n - 2) / 3))))
-  p$file      <- sprintf("../trajectories/T%03d_%d_rest%d.csv", p$trialid, p$trialType, p$rest_k)
-    
-  return(p)
-}
-
-for (i in 1:100) {
-  p <- create.protocol(i)
-  write.csv(p,sprintf("../data/exp1/protocols/P%03d.csv", i), row.names = F)
-}

### 2018-07-02 R/exp1a/01-parsedata.R

@@ -1,0 +1,11 @@
+rm(list = ls())
+
+pth <- here::here("..","data","exp1a","responses")
+
+files <- list.files(pth, pattern = "*.csv", full.names = T)
+
+df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
+
+str(df)
+
+saveRDS(df,file = "../data/exp1a/responses/responses_150330.rds")

### 2018-07-02 R/exp1a/create-protocols.R

@@ -1,0 +1,29 @@
+rm(list = ls())
+
+masterseed <- 98765
+
+create.protocol <- function(pid) {
+  set.seed(masterseed + pid)
+  n <- 194
+  p <- data.frame(pid = rep(pid, n),
+                  block = c(0,0,rep(1:4, each = (n - 2) / 4)),
+                  trial = 1:n,
+                  file = character(n),
+                  trialid = numeric(n),
+                  trialType = numeric(n),                  
+                  rest_k = numeric(n),
+                  stringsAsFactors = F)
+  ks <- c(1, 2, 4, 8, 16, 32, 64, 128)
+  stopifnot((n - 2) %% length(ks) == 0)
+  p$trialType <- c(sample(ks,2), sample(rep(ks, each = (n - 2) / length(ks)))) 
+  p$trialid   <- sample(n) 
+  p$rest_k   <- c(4,64,sample(c(rep(4,(n - 2) / 3), rep(16, (n - 2) / 3), rep(64,(n - 2) / 3))))
+  p$file      <- sprintf("../trajectories/T%03d_%d_rest%d.csv", p$trialid, p$trialType, p$rest_k)
+    
+  return(p)
+}
+
+for (i in 1:100) {
+  p <- create.protocol(i)
+  write.csv(p,sprintf("../data/exp1/protocols/P%03d.csv", i), row.names = F)
+}

### 2018-07-02 R/exp1b/01-parsedata.R

@@ -1,0 +1,11 @@
+rm(list = ls())
+
+pth <- here::here("..","data","exp1b","responses")
+
+files <- list.files(pth, pattern = "*.csv", full.names = T)
+
+df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
+
+str(df)
+df <- filter(df, subject != 1)
+saveRDS(df,file = "../data/exp1b/responses/responses_150622.rds")

### 2018-07-02 R/exp2/01-parsedata.R

@@ -1,11 +1,0 @@
-rm(list = ls())
-
-pth <- "../data/exp2/responses/"
-
-files <- list.files(pth, pattern = "*.csv", full.names = T)
-
-df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
-
-str(df)
-df <- filter(df, subject != 1)
-save(df,file = "../data/exp2/responses/responses_150622.RData")

### 2018-07-02 R/exp2/create-protocols.R

@@ -1,33 +1,0 @@
-rm(list = ls())
-
-masterseed <- 198765
-
-create.protocol <- function(pid) {
-  set.seed(masterseed + pid)
-  n <- 202
-  p <- data.frame(pid = rep(pid, n),
-                  block = c(0,0,rep(1:4, each = (n - 2) / 4)),
-                  trial = 1:n,
-                  file = character(n),
-                  trialid = numeric(n),
-                  trialType = numeric(n),                  
-                  rest_k = numeric(n),
-                  stringsAsFactors = F)
-  ks <- c(2, 4, 8, 16, 64)
-  stopifnot((n - 2) %% length(ks) == 0)
-  
-  dfx <- rbind(expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks)) 
-  dfx <- dfx[sample(1:nrow(dfx)),]
-  
-  p$trialType <- c(sample(ks,2), dfx[,1]) 
-  p$trialid   <- sample(n) 
-  p$rest_k   <- c(sample(ks,2), dfx[,2])
-  p$file      <- sprintf("../trajectories/T%03d_%d_rest%d.csv", p$trialid, p$trialType, p$rest_k)
-    
-  return(p)
-}
-
-for (i in 1:100) {
-  p <- create.protocol(i)
-  write.csv(p,sprintf("../data/exp2/protocols/P%03d.csv", i), row.names = F)
-}

### 2018-07-02 R/exp2a/01-parsedata.R

@@ -1,0 +1,15 @@
+rm(list = ls())
+
+pth <- here::here("..","data","exp2a","responses")
+
+files <- list.files(pth, pattern = "*.csv", full.names = T)
+
+df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
+
+df$restk <- as.numeric(gsub(".*rest(.*)\\.csv","\\1",df$file))
+df$type  <- as.numeric(gsub(".*_(.*)_rest.*","\\1",df$file))
+
+str(df)
+
+
+saveRDS(df,file = "../data/exp2a/responses/responses_150410.rds")

### 2018-07-02 R/exp2b/01-parsedata.R

@@ -1,0 +1,12 @@
+rm(list = ls())
+
+
+pth <- here::here("..","data","exp2b","responses")
+
+files <- list.files(pth, pattern = "*.csv", full.names = T)
+
+df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
+
+str(df)
+
+saveRDS(df,file = "../data/exp2b/responses/responses_171023.rds")

### 2018-07-02 R/exp2b/create-protocols.R

@@ -1,0 +1,33 @@
+rm(list = ls())
+
+masterseed <- 198765111
+
+create.protocol <- function(pid) {
+  set.seed(masterseed + pid)
+  n <- 202
+  p <- data.frame(pid = rep(pid, n),
+                  block = c(0,0,rep(1:4, each = (n - 2) / 4)),
+                  trial = 1:n,
+                  file = character(n),
+                  trialid = numeric(n),
+                  trialType = numeric(n),                  
+                  rest_k = numeric(n),
+                  stringsAsFactors = F)
+  ks <- c(0.005, 0.01, 0.02, 0.04, 0.08)
+  stopifnot((n - 2) %% length(ks) == 0)
+  
+  dfx <- rbind(expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks)) 
+  dfx <- dfx[sample(1:nrow(dfx)),]
+  
+  p$trialType <- c(sample(ks,2), dfx[,1]) 
+  p$trialid   <- sample(n) 
+  p$rest_k   <- c(sample(ks,2), dfx[,2])
+  p$file      <- sprintf("../trajectories/T%03d_%.03f_rest%.03f.csv", p$trialid, p$trialType, p$rest_k)
+    
+  return(p)
+}
+
+for (i in 1:100) {
+  p <- create.protocol(i)
+  write.csv(p,sprintf("../data/exp4/protocols/P%03d.csv", i), row.names = F)
+}

### 2018-07-02 R/exp3/01-parsedata.R

@@ -1,14 +1,0 @@
-rm(list = ls())
-
-pth <- "../data/exp3/responses/"
-
-files <- list.files(pth, pattern = "*.csv", full.names = T)
-
-df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
-
-df$restk <- as.numeric(gsub(".*rest(.*)\\.csv","\\1",df$file))
-df$type  <- as.numeric(gsub(".*_(.*)_rest.*","\\1",df$file))
-
-str(df)
-
-save(df,file = "../data/exp3/responses/responses_150410.RData")

### 2018-07-02 R/exp3/create-protocols.R

@@ -1,29 +1,0 @@
-rm(list = ls())
-
-masterseed <- 18766
-
-create.protocol <- function(pid) {
-  set.seed(masterseed + pid)
-  n <- 198
-  p <- data.frame(pid = rep(pid, n),
-                  block = c(0,0,rep(1:4, each = (n - 2) / 4)),
-                  trial = 1:n,
-                  file = character(n),
-                  trialid = numeric(n),
-                  trialType = numeric(n),                  
-                  rest_k = numeric(n),
-                  stringsAsFactors = F)
-  ks <- c(0.005, 0.01, 0.02, 0.03, 0.04, 0.06, 0.08)
-  stopifnot((n - 2) %% length(ks) == 0)
-  p$trialType <- c(sample(ks,2), sample(rep(ks, each = (n - 2) / length(ks)))) 
-  p$trialid   <- sample(n) 
-  p$rest_k   <- c(0.02,0.04,sample(c(rep(0.02,(n - 2) / 2), rep(0.04, (n - 2) / 2))))
-  p$file      <- sprintf("../trajectories/T%03d_%.03f_rest%.03f.csv", p$trialid, p$trialType, p$rest_k)
-    
-  return(p)
-}
-
-for (i in 1:100) {
-  p <- create.protocol(i)
-  write.csv(p,sprintf("../data/exp3/protocols/P%03d.csv", i), row.names = F)
-}

### 2018-07-02 R/exp4/01-parsedata.R

@@ -1,11 +1,0 @@
-rm(list = ls())
-
-pth <- "../data/exp4/responses/"
-
-files <- list.files(pth, pattern = "*.csv", full.names = T)
-
-df <- do.call("rbind",lapply(files,FUN=function(f) {read.csv(f, skip = 1, stringsAsFactors = F)}))
-
-str(df)
-
-save(df,file = "../data/exp4/responses/responses_171023.RData")

### 2018-07-02 R/exp4/create-protocols.R

@@ -1,33 +1,0 @@
-rm(list = ls())
-
-masterseed <- 198765111
-
-create.protocol <- function(pid) {
-  set.seed(masterseed + pid)
-  n <- 202
-  p <- data.frame(pid = rep(pid, n),
-                  block = c(0,0,rep(1:4, each = (n - 2) / 4)),
-                  trial = 1:n,
-                  file = character(n),
-                  trialid = numeric(n),
-                  trialType = numeric(n),                  
-                  rest_k = numeric(n),
-                  stringsAsFactors = F)
-  ks <- c(0.005, 0.01, 0.02, 0.04, 0.08)
-  stopifnot((n - 2) %% length(ks) == 0)
-  
-  dfx <- rbind(expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks),expand.grid(ks, ks)) 
-  dfx <- dfx[sample(1:nrow(dfx)),]
-  
-  p$trialType <- c(sample(ks,2), dfx[,1]) 
-  p$trialid   <- sample(n) 
-  p$rest_k   <- c(sample(ks,2), dfx[,2])
-  p$file      <- sprintf("../trajectories/T%03d_%.03f_rest%.03f.csv", p$trialid, p$trialType, p$rest_k)
-    
-  return(p)
-}
-
-for (i in 1:100) {
-  p <- create.protocol(i)
-  write.csv(p,sprintf("../data/exp4/protocols/P%03d.csv", i), row.names = F)
-}

### 2018-07-02 R/manuscript_app.Rmd
code polishing
- data are loaded using here package
- used libraries are installed if needed
- all ANOVA's are computed

---
title: "manuscript - JEP:HPP"
author: "Filip Dechterenko"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

## Load libraries

```{r load libraries}
here::set_here("../data")

if (!require(tidyverse)) {install.packages("tidyverse"); library(tidyverse)}
if (!require(ez)) {install.packages("ez"); library(ez)}
if (!require(psyphy)) {install.packages("psyphy"); library(psyphy)}

if (!require(here)) {install.packages("here")}

theme_set(theme_bw(16))
source("tools.R")

```

# Experiment 1a

```{r load data - exp 1a}
df_exp1a <- readRDS(here::here("..","data","exp1a","responses","responses_150330.rds")) %>% 
  filter(block != 0) %>% 
  filter(restk != "64") %>% # originally, we colledcted three levels of variaiblity, but the condition with kappa=64 showed similar results as kappa = 16
  as_data_frame() %>% 
  mutate(restk2 = recode(restk, `4` = "Brownian-like", `16` = "Ballistic-like"))

participants_exp1a <- read.csv(here::here("..","data","exp1a","participants_150526.csv"))

```

## Participant info
```{r participant info exp 1a}
table(participants_exp1a$gender)
c(mean(participants_exp1a$age), sd(participants_exp1a$age)) %>% round(2)
```

## Results

```{r}
df_exp1a %>% 
  group_by(restk) %>% 
  summarize(accuracy_mean = mean(accuracy, na.rm = T)) %>% 
  knitr::kable(digits = 2)

df_exp1a %>% 
  group_by(restk,type) %>% 
  summarize(accuracy_mean = mean(accuracy, na.rm = T)) %>% 
  knitr::kable(digits = 2)

```

## Figure 1

```{r Figure 1}
traj_k64 <- read.table("../data/exp1/trajectories/T001_64_rest4.csv") %>% select(x = V1,y = V2) %>% as_data_frame()
p1 <- traj_k64 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15) +
  ggtitle("Ballistic-like")

traj_k4 <- read.table("../data/exp1/trajectories/T001_4_rest4.csv") %>% select(x = V3,y = V4) %>% as_data_frame()
p2 <- traj_k4 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15)+
  ggtitle("Brownian-like")
gridExtra::grid.arrange(p1,p2, ncol = 2)
ggsave("Figure1_ballistic.png", p1, width = 6, height = 6)
ggsave("Figure1_brownian.png", p2, width = 6, height = 6)
ggsave("Figure1_ballistic.eps", p1, width = 6, height = 6)
ggsave("Figure1_brownian.eps", p2, width = 6, height = 6)
```

## Figure 2

```{r Figure 2}

plot_fig2 <- function(restk_var, ggtit) {
  df_exp1a %>%
  filter(restk == restk_var) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,8,16,32,64,128),labels = c("1","8","16","32","64","128"), trans = "log2") + 
  geom_vline(xintercept = restk_var, linetype = 2) +
  ggtitle(ggtit)
}

p1 <- plot_fig2(4, "Brownian-like-distractors")
p2 <- plot_fig2(16, "Ballistic-like-distractors")

gridExtra::grid.arrange(p1,p2, ncol = 2)

ggsave("plots/Figure2_brownian.png", p1, width = 6, height = 6)
ggsave("plots/Figure2_ballistic.png", p2, width = 6, height = 6)
ggsave("plots/Figure2_brownian.eps", p1, width = 6, height = 6)
ggsave("plots/Figure2_ballistic.eps", p2, width = 6, height = 6)
```

```{r fitting weibull}

df.pf <- df_exp1a %>% 
  filter(restk2 == "Ballistic-like", type %in% c(2,4,8,16,32))

df.pf2 <- df.pf %>% 
  group_by(type) %>% 
  summarise(yes = sum(accuracy), no = n() - sum(accuracy), accuracy = 1 - mean(accuracy))

pf <- psyfun.2asym(cbind(yes, no) ~ type, data = df.pf2, link = weib.2asym, init.g = 0.125, init.lam = 0.05 )

x <- seq(-2,32,0.01)
y <- predict(pf, data.frame(type = x), type="response")

dfmodel <- data.frame(x, y)

p <- ggplot(data = dfmodel, aes(x = x, y = y)) + geom_line(color="red", size =1.5) + stat_summary(data = df.pf, aes(x = type, y=accuracy),fun.data = "mean_cl_boot", size = 1) + scale_x_continuous(expression("Target's"~kappa), breaks = df.pf2$type) + ylab("Accuracy")
p

```

## Overall differences

```{r}
df_exp1 %>% 
  filter(restk2 == "Brownian-like") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

df_exp1 %>% 
  filter(restk2 == "Ballistic-like") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()
```

## Tests with baseline

```{r}
df_exp1a %>% 
  group_by(type, restk,subject) %>% 
  summarize(accuracy = mean(accuracy)) %>% 
  group_by(restk, type) %>% 
  filter(accuracy < 1) %>% 
  do(t.test(.$accuracy, mu = .125) %>% 
       broom::tidy()) %>% 
  mutate(p.value = round(p.value, 3)) %>% 
  knitr::kable()
```

## Difference between symmetrical cases
```{r}
df_exp1a %>% 
  filter((restk == 4 & type == 16) |(restk == 16 & type == 4)) %>% 
  ez::ezANOVA(
        dv = accuracy,
        wid = subject,
        within = restk, 
        detailed = T) %>% 
  apa::anova_apa()

```

# Experiment 1b

```{r load data - experiment 1b}
load(here::here("..","data","exp1b","responses","responses_150622.RData"))
df_exp1b <- filter(df, block != 0)

participants_exp2 <- read.csv(here::here("..","data","exp1b","participants_150526.csv"), fileEncoding = "UTF8")

df2_exp1b <- rbind(df_exp1b,df_exp1b)
df2_exp1b$version <- 2
df2_exp1b$version[1:nrow(df_exp1b)] <- 1

# this is a little hack, just to make a correct ggplot with one line
tmp <- df_exp1b$restk
df2_exp1b$restk[df2_exp1b$version == 2] <- df_exp1b$type
df2_exp1b$type[df2_exp1b$version == 2] <- tmp

df2_exp1b$version <- factor(df2_exp1b$version, labels = c("fix distractors' k", "fix target's k"))
```

## Participant info
```{r}
table(participants_exp2$gender)
c(mean(participants_exp2$age), sd(participants_exp2$age)) %>% round(2)
```

## Figure 3

```{r plots experiment 2}
plot_fig3 <- function(restk_var, show_legend = F) {

  p <- df2_exp1b %>%
  filter(restk == restk_var) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous(expression("Variable"~kappa~" (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
  scale_linetype_manual(values = c(2,1)) +
  geom_vline(xintercept = restk_var, linetype = 2) +
  ggtitle(bquote("Fixed "~kappa~"= "~.(restk_var)))

  if (show_legend) {
    p 
  } else {
    p + theme(legend.position="none")
  }

}

p_k2 <- plot_fig3(2)
p_k4 <- plot_fig3(4)
p_k8 <- plot_fig3(8)
p_k16 <- plot_fig3(16)
p_k64 <- plot_fig3(64)
p_k64 <- plot_fig3(64, show_legend = T)

gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 5)
ggsave("plots/Fig3_k2.eps", p_k2, width = 6, height = 6)
ggsave("plots/Fig3_k4.eps", p_k4, width = 6, height = 6)
ggsave("plots/Fig3_k8.eps", p_k8, width = 6, height = 6)
ggsave("plots/Fig3_k16.eps", p_k16, width = 6, height = 6)
ggsave("plots/Fig3_k64.eps", p_k64, width = 6, height = 6)
ggsave("plots/Fig3_k64_legend.eps", p_k64_legend, width = 6, height = 6)
# final plot was created in inkscape
```

## Compute the asymmetry

We run multiple within subject aova

```{r compute the assymetry - exp1b, warning=F}
df3_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(p=compute.p(.))

df3_exp1b$p <- unlist(df3_exp1b$p) %>% round(3)
df4_exp2 <- df2_exp1b %>% group_by(type, restk) %>% do(ges=compute.des(.))
df4_exp2$ges <- unlist(df4_exp2$ges) %>% round(2)
df3_exp1b$ges <- df4_exp2$ges

df5_exp2 <- df2_exp1b %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
  group_by(type, restk) %>%
  summarize(acc_diff = accuracy[version == "fix distractors' k"] - accuracy[version == "fix target's k"])

m <- matrix(df3_exp1b$ges, nrow = 5)
rownames(m) <- levels(df_exp1b$type)
colnames(m) <- levels(df_exp1b$type)
m[upper.tri(m,diag = T)] <- NA

df3_exp1b$ges <- as.vector(m)

m <- matrix(df3_exp1b$p, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1b$p <- as.vector(m)

m <- matrix(df5_exp2$acc_diff, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1b$acc_diff <- as.vector(m)

df3_exp1b$target_lower_than_dist <- df3_exp1b$acc_diff < 0
df3_exp1b %>% filter(target_lower_than_dist)

df3_exp1b %>% filter(p < .05)
```

Test with baseline

```{r}
df_exp1b %>% group_by(type, restk,subject) %>% summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>% filter(accuracy <1) %>% do(t.test(.$accuracy, mu = .125) %>% broom::tidy()) %>% mutate(p.value = round(p.value, 3)) %>% knitr::kable()
```

# Experiment 2a

```{r load data - exp 2a}
load(here::here("..","data","exp2a","responses","responses_150410.RData"))
df_exp2a <- filter(df, block != 0) 
df_exp2a <- df_exp2a %>% mutate(restk = restk * 100, type = type * 100)
participants <- read.csv("../data/exp2/participants_171023.csv")
```

## Participant info
```{r exp3 participant info}
table(participants_exp3$gender)
c(mean(participants_exp3$age), sd(participants_exp3$age)) %>% round(2)
```

## Results

```{r}
df_exp2a %>% group_by(restk) %>% summarize(accuracy_mean = mean(accuracy, na.rm = T) %>% round(2))
```

## Figure 4

```{r}
p1 <- df_exp2a %>%
  filter(restk == 2) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  geom_vline(xintercept = 2, linetype = 2) +
  scale_x_continuous("Target's speed (log scale)",breaks = c(0.5,1,2,3,4,6,8),labels = c("0.5","1","2","3","4","6","8"), trans = "log2") + 
  ggtitle("Slow-moving-distractors")
p2 <- df_exp2a %>%
  filter(restk == 4) %>%
  ggplot(aes(x = type, y = accuracy)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
  geom_hline(yintercept=0.125) + 
  theme(aspect.ratio = 1)  + 
  ylab("Accuracy") + 
  ylim(0,1)+
  geom_vline(xintercept = 4, linetype = 2) +
  scale_x_continuous("Target's speed (log scale)",breaks = c(0.5,1,2,3,4,6,8),labels = c("0.5","1","2","3","4","6","8"), trans = "log2") + 
  ggtitle("Fast-moving-distractors")
gridExtra::grid.arrange(p1,p2, ncol = 2)

ggsave("plots/Figure4_slow.png", p1, width = 6, height = 6)
ggsave("plots/Figure4_fast.png", p2, width = 6, height = 6)
ggsave("plots/Figure4_slow.eps", p1, width = 6, height = 6)
ggsave("plots/Figure4_fast.eps", p2, width = 6, height = 6)
```

## Statistics

```{r exp 3 - statistics}
df_exp2a %>% group_by(restk) %>% summarize(acc = mean(accuracy) * 100, sd = sd(accuracy) *100)
```

Difference between symmetrical cases
```{r}
df_sym <- df_exp2a %>% filter((restk == 2 & type == 4) |(restk == 4 & type == 2))
ez::ezANOVA(df_sym,
        dv=accuracy,
        wid = subject,
        within = restk)
ez::ezStats(df_sym,
        dv=accuracy,
        wid = subject,
        within = restk)

```

Test with baseline

```{r}
df_exp2a %>% group_by(type, restk,subject) %>% summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>% filter(accuracy <1) %>% do(t.test(.$accuracy, mu = .125) %>% broom::tidy()) %>% mutate(p.value = round(p.value, 3)) %>% knitr::kable()
```

# Experiment 2b

```{r load data - exp 2b}
load("../data/exp2_fin/responses/responses_171023.RData")

df_exp2b <- filter(df, block != 0) 
df_exp2b <- df_exp2b %>% mutate(restk = restk * 100, type = type * 100)
rm(df)

participants_exp4 <- read.csv("../data/exp2_fin/participants_171023.csv")

df2_exp1bb <- rbind(df_exp2b, df_exp2b)
df2_exp1bb$version <- 2
df2_exp1bb$version[1:nrow(df_exp2b)] <- 1

# this is a little hack, just to make a correct ggplot with one line
tmp <- df_exp2b$restk
df2_exp1bb$restk[df2_exp1bb$version == 2] <- df_exp2b$type
df2_exp1bb$type[df2_exp1bb$version == 2] <- tmp

df2_exp1bb$version <- factor(df2_exp1bb$version, labels = c("fix distractors' speed", "fix target's speed"))
```

## Participant info
```{r exp4 - participants info}
table(participants_exp4$gender)
c(mean(participants_exp4$age), sd(participants_exp4$age)) %>% round(2)
```

## Figure 5

```{r Figure 5}

p_sp05 <- df2_exp1bb %>%
  filter(restk == .5) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = .5, linetype = 2) +
  ggtitle(expression("Fixed speed = 0.5"*degree*"/s"))

p_sp1 <- df2_exp1bb %>%
  filter(restk == 1) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 1, linetype = 2) +
  ggtitle(expression("Fixed speed = 1"*degree*"/s"))

p_sp2 <- df2_exp1bb %>%
  filter(restk == 2) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 2, linetype = 2) +
  ggtitle(expression("Fixed speed = 2"*degree*"/s"))

p_sp4 <- df2_exp1bb %>%
  filter(restk == 4) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 4, linetype = 2) +
  ggtitle(expression("Fixed speed = 4"*degree*"/s"))

p_sp8 <- df2_exp1bb %>%
  filter(restk == 8) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  theme(legend.position="none") +
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 8, linetype = 2) +
  ggtitle(expression("Fixed speed = 8"*degree*"/s"))

p_sp8_legend <- df2_exp1bb %>%
  filter(restk == 8) %>%
  ggplot(aes(x = type, y = accuracy, group = version)) + 
  #facet_grid(~ restk) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
  geom_hline(yintercept=0.125) +
  theme(aspect.ratio = 1) + 
  ylab("Accuracy") + 
  ylim(0,1)+
  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                     trans = "log2") + 
  geom_vline(xintercept = 8, linetype = 2) +
  ggtitle(expression("Fixed speed = 8"*degree*"/s"))

gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 5)
ggsave("plots/Fig5_sp05.eps", p_sp05, width = 6, height = 6)
ggsave("plots/Fig5_sp1.eps", p_sp1, width = 6, height = 6)
ggsave("plots/Fig5_sp2.eps", p_sp2, width = 6, height = 6)
ggsave("plots/Fig5_sp4.eps", p_sp4, width = 6, height = 6)
ggsave("plots/Fig5_sp8.eps", p_sp8, width = 6, height = 6)
ggsave("plots/Fig5_sp8_legend.eps", p_sp8_legend, width = 6, height = 6)
# final plot was created in inkscape
```

## Compute the asymmetry

```{r compute the assymetry, warning=F}
df3_exp1bb <- df2_exp1bb %>% group_by(type, restk) %>% do(p=compute.p(.))

df3_exp1bb$p <- unlist(df3_exp1bb$p) %>% round(3)
df4_exp4 <- df2_exp1bb %>% group_by(type, restk) %>% do(ges=compute.des(.))
df4_exp4$ges <- unlist(df4_exp4$ges) %>% round(2)
df3_exp1bb$ges <- df4_exp4$ges

df5_exp4 <- df2_exp1bb %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
  group_by(type, restk) %>%
  summarize(acc_diff = accuracy[version == "fix distractors' speed"] - accuracy[version == "fix target's speed"])

m <- matrix(df3_exp1bb$ges, nrow = 5)
rownames(m) <- levels(df_exp2b$type)
colnames(m) <- levels(df_exp2b$type)
m[upper.tri(m,diag = T)] <- NA

df3_exp1bb$ges <- as.vector(m)

m <- matrix(df3_exp1bb$p, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1bb$p <- as.vector(m)

m <- matrix(df5_exp4$acc_diff, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1bb$acc_diff <- as.vector(m)

df3_exp1bb$target_lower_than_dist <- df3_exp1bb$acc_diff < 0
df3_exp1bb %>% filter(target_lower_than_dist)

df3_exp1bb %>% filter(p < 0.05)

differencies <- df3_exp1bb %>% filter(target_lower_than_dist)  %>% .$acc_diff *-1
differencies %>% range() %>% round(2)

```

### 2018-07-02 R/tools.R
create functions for figures

@@ -67,3 +67,79 @@ compute.des <- function(dfx) {
   return(diff(means$Mean))
   
 }
+
+plot_fig2 <- function(restk_var, ggtit) {
+  df_exp1a %>%
+    filter(restk == restk_var) %>%
+    ggplot(aes(x = type, y = accuracy)) + 
+    stat_summary(fun.data = "mean_cl_boot") + 
+    stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
+    geom_hline(yintercept=0.125) + 
+    theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
+    ylab("Accuracy") + 
+    ylim(0,1)+
+    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,8,16,32,64,128),labels = c("1","8","16","32","64","128"), trans = "log2") + 
+    geom_vline(xintercept = restk_var, linetype = 2) +
+    ggtitle(ggtit)
+}
+
+plot_fig3 <- function(restk_var, show_legend = F) {
+  
+  p <- df2_exp1b %>%
+    filter(restk == restk_var) %>%
+    ggplot(aes(x = type, y = accuracy, group = version)) + 
+    #facet_grid(~ restk) + 
+    stat_summary(fun.data = "mean_cl_boot") + 
+    stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
+    geom_hline(yintercept=0.125) +
+    theme(aspect.ratio = 1) + 
+    ylab("Accuracy") + 
+    ylim(0,1)+
+    scale_x_continuous(expression("Variable"~kappa~" (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
+    scale_linetype_manual(values = c(2,1)) +
+    geom_vline(xintercept = restk_var, linetype = 2) +
+    ggtitle(bquote("Fixed "~kappa~"= "~.(restk_var)))
+  
+  if (show_legend) {
+    p 
+  } else {
+    p + theme(legend.position="none")
+  }
+  
+}
+
+plot_fig4 <- function(restspd, ggtit) {
+  df_exp2a %>%
+    filter(restk == restspd) %>%
+    ggplot(aes(x = type, y = accuracy)) + 
+    stat_summary(fun.data = "mean_cl_boot") + 
+    stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
[…]

### 2018-07-02 R/manuscript_app.Rmd
finish code polishing

@@
 ---
-title: "manuscript - JEP:HPP"
+title: "manuscript - APP"
 author: "Filip Dechterenko"
@@
 
-```{r load libraries}
-here::set_here("../data")
+```{r load libraries, warning=F, message=F}
 
@@
 
+data_pth <- here::here("..", "data")
+plot_pth <- here::here("..", "plots")
+
+if(!dir.exists(plot_pth)) {
+  dir.create(plot_pth)
+}
 ```
@@
 ```{r load data - exp 1a}
-df_exp1a <- readRDS(here::here("..","data","exp1a","responses","responses_150330.rds")) %>% 
+df_exp1a <- readRDS(file.path(data_pth,"exp1a","responses","responses_150330.rds")) %>% 
   filter(block != 0) %>% 
@@
 
-participants_exp1a <- read.csv(here::here("..","data","exp1a","participants_150526.csv"))
+participants_exp1a <- read.csv(file.path(data_pth,"exp1a","participants_150526.csv"))
 
@@
 
-```{r}
+```{r exp1 results accuracy}
 df_exp1a %>% 
@@
 ```{r Figure 1}
-traj_k64 <- read.table("../data/exp1/trajectories/T001_64_rest4.csv") %>% select(x = V1,y = V2) %>% as_data_frame()
+traj_k64 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_64_rest4.csv")) %>% select(x = V1,y = V2) %>% as_data_frame()
 p1 <- traj_k64 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15) +
@@
 
-traj_k4 <- read.table("../data/exp1/trajectories/T001_4_rest4.csv") %>% select(x = V3,y = V4) %>% as_data_frame()
+traj_k4 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_4_rest4.csv")) %>% select(x = V3,y = V4) %>% as_data_frame()
 p2 <- traj_k4 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15)+
@@
 gridExtra::grid.arrange(p1,p2, ncol = 2)
-ggsave("Figure1_ballistic.png", p1, width = 6, height = 6)
-ggsave("Figure1_brownian.png", p2, width = 6, height = 6)
-ggsave("Figure1_ballistic.eps", p1, width = 6, height = 6)
-ggsave("Figure1_brownian.eps", p2, width = 6, height = 6)
+
+ggsave(file.path(plot_pth, "Figure1_ballistic.png"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure1_brownian.png"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure1_ballistic.eps"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure1_brownian.eps"), p2, width = 6, height = 6)
 ```
@@
 
-plot_fig2 <- function(restk_var, ggtit) {
-  df_exp1a %>%
-  filter(restk == restk_var) %>%
-  ggplot(aes(x = type, y = accuracy)) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
-  geom_hline(yintercept=0.125) + 
-  theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,8,16,32,64,128),labels = c("1","8","16","32","64","128"), trans = "log2") + 
-  geom_vline(xintercept = restk_var, linetype = 2) +
-  ggtitle(ggtit)
-}
-
 p1 <- plot_fig2(4, "Brownian-like-distractors")
@@
 
-ggsave("plots/Figure2_brownian.png", p1, width = 6, height = 6)
-ggsave("plots/Figure2_ballistic.png", p2, width = 6, height = 6)
-ggsave("plots/Figure2_brownian.eps", p1, width = 6, height = 6)
-ggsave("plots/Figure2_ballistic.eps", p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure2_brownian.png"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure2_ballistic.png"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure2_brownian.eps"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure2_ballistic.eps"), p2, width = 6, height = 6)
 ```
 
-```{r fitting weibull}
+```{r exp1a - fitting weibull}
 
@@
 
-```{r}
-df_exp1 %>% 
+```{r exp 1a - overall differences, warning=F, message = F}
+df_exp1a %>% 
   filter(restk2 == "Brownian-like") %>% 
@@
 
-df_exp1 %>% 
+df_exp1a %>% 
   filter(restk2 == "Ballistic-like") %>% 
@@
 
-```{r}
+```{r exp 1a - test vs baseline}
 df_exp1a %>% 
@@
 ## Difference between symmetrical cases
-```{r}
+```{r exp1a - difference between symmetrical case, warning=F, message = F}
 df_exp1a %>% 
@@
 
-```{r load data - experiment 1b}
-load(here::here("..","data","exp1b","responses","responses_150622.RData"))
-df_exp1b <- filter(df, block != 0)
+```{r exp1b  - load data}
+df_exp1b <- readRDS(file.path(data_pth,"exp1b","responses","responses_150622.rds")) %>% 
+  filter(block != 0)
 
-participants_exp2 <- read.csv(here::here("..","data","exp1b","participants_150526.csv"), fileEncoding = "UTF8")
+participants_exp1b <- read.csv(file.path(data_pth,"exp1b","participants_150526.csv"), fileEncoding = "UTF8")
 
@@
 ```{r}
-table(participants_exp2$gender)
-c(mean(participants_exp2$age), sd(participants_exp2$age)) %>% round(2)
+table(participants_exp1b$gender)
+c(mean(participants_exp1b$age), sd(participants_exp1b$age)) %>% round(2)
 ```
@@
 ```{r plots experiment 2}
-plot_fig3 <- function(restk_var, show_legend = F) {
-
-  p <- df2_exp1b %>%
-  filter(restk == restk_var) %>%
-  ggplot(aes(x = type, y = accuracy, group = version)) + 
-  #facet_grid(~ restk) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
-  geom_hline(yintercept=0.125) +
-  theme(aspect.ratio = 1) + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  scale_x_continuous(expression("Variable"~kappa~" (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
-  scale_linetype_manual(values = c(2,1)) +
-  geom_vline(xintercept = restk_var, linetype = 2) +
-  ggtitle(bquote("Fixed "~kappa~"= "~.(restk_var)))
-
-  if (show_legend) {
-    p 
-  } else {
-    p + theme(legend.position="none")
-  }
-
-}
 
@@
 p_k64 <- plot_fig3(64)
-p_k64 <- plot_fig3(64, show_legend = T)
+p_k64_legend <- plot_fig3(64, show_legend = T)
 
-gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 5)
-ggsave("plots/Fig3_k2.eps", p_k2, width = 6, height = 6)
-ggsave("plots/Fig3_k4.eps", p_k4, width = 6, height = 6)
-ggsave("plots/Fig3_k8.eps", p_k8, width = 6, height = 6)
-ggsave("plots/Fig3_k16.eps", p_k16, width = 6, height = 6)
-ggsave("plots/Fig3_k64.eps", p_k64, width = 6, height = 6)
-ggsave("plots/Fig3_k64_legend.eps", p_k64_legend, width = 6, height = 6)
+gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
+ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
 # final plot was created in inkscape
@@
 df3_exp1b$p <- unlist(df3_exp1b$p) %>% round(3)
-df4_exp2 <- df2_exp1b %>% group_by(type, restk) %>% do(ges=compute.des(.))
-df4_exp2$ges <- unlist(df4_exp2$ges) %>% round(2)
-df3_exp1b$ges <- df4_exp2$ges
+df4_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(ges=compute.des(.))
+df4_exp1b$ges <- unlist(df4_exp1b$ges) %>% round(2)
+df3_exp1b$ges <- df4_exp1b$ges
 
-df5_exp2 <- df2_exp1b %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
+df5_exp1b <- df2_exp1b %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
   group_by(type, restk) %>%
@@
 
-m <- matrix(df5_exp2$acc_diff, nrow = 5)
+m <- matrix(df5_exp1b$acc_diff, nrow = 5)
 m[upper.tri(m, diag = T)] <- NA
@@
 
-Test with baseline
+## Test with baseline
 
 ```{r}
-df_exp1b %>% group_by(type, restk,subject) %>% summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>% filter(accuracy <1) %>% do(t.test(.$accuracy, mu = .125) %>% broom::tidy()) %>% mutate(p.value = round(p.value, 3)) %>% knitr::kable()
+df_exp1b %>% 
+  group_by(type, restk, subject) %>% 
+  summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>%
+  filter(accuracy < 1) %>% 
+  do(t.test(.$accuracy, mu = .125) %>% 
+       broom::tidy()) %>% 
+  mutate(p.value = round(p.value, 3)) %>% 
+  knitr::kable()
 ```
@@
 ```{r load data - exp 2a}
-load(here::here("..","data","exp2a","responses","responses_150410.RData"))
-df_exp2a <- filter(df, block != 0) 
-df_exp2a <- df_exp2a %>% mutate(restk = restk * 100, type = type * 100)
-participants <- read.csv("../data/exp2/participants_171023.csv")
+df_exp2a <- readRDS(file.path(data_pth,"exp2a","responses","responses_150410.rds")) %>% 
+  filter(block != 0) %>% 
+  mutate(restk = restk * 100, type = type * 100) %>% 
+  mutate(restk2 = recode(restk, `2` = "Slow-moving-distractors", `4` = "Fast-moving-distractors"))
+
+participants_exp2a <- read.csv(file.path(data_pth,"exp2a","participants_171023.csv"))
 ```
@@
 ## Participant info
-```{r exp3 participant info}
-table(participants_exp3$gender)
-c(mean(participants_exp3$age), sd(participants_exp3$age)) %>% round(2)
+
+```{r exp2a - participant info}
+table(participants_exp2a$gender)
+c(mean(participants_exp2a$age), sd(participants_exp2a$age)) %>% round(2)
 ```
@@
 
-```{r}
-df_exp2a %>% group_by(restk) %>% summarize(accuracy_mean = mean(accuracy, na.rm = T) %>% round(2))
+```{r exp2a - results accuracy}
+df_exp2a %>% 
+  group_by(restk) %>% 
+  summarize(accuracy_mean = mean(accuracy, na.rm = T)) %>% knitr::kable(digits = 2)
 ```
@@
 
-```{r}
-p1 <- df_exp2a %>%
-  filter(restk == 2) %>%
-  ggplot(aes(x = type, y = accuracy)) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
-  geom_hline(yintercept=0.125) + 
-  theme(aspect.ratio = 1) + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  geom_vline(xintercept = 2, linetype = 2) +
-  scale_x_continuous("Target's speed (log scale)",breaks = c(0.5,1,2,3,4,6,8),labels = c("0.5","1","2","3","4","6","8"), trans = "log2") + 
-  ggtitle("Slow-moving-distractors")
-p2 <- df_exp2a %>%
-  filter(restk == 4) %>%
-  ggplot(aes(x = type, y = accuracy)) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
-  geom_hline(yintercept=0.125) + 
-  theme(aspect.ratio = 1)  + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  geom_vline(xintercept = 4, linetype = 2) +
-  scale_x_continuous("Target's speed (log scale)",breaks = c(0.5,1,2,3,4,6,8),labels = c("0.5","1","2","3","4","6","8"), trans = "log2") + 
-  ggtitle("Fast-moving-distractors")
+```{r Figure 4}
+
+p1 <- plot_fig4(2, ggtit = "Slow-moving-distractors")
+
+p2 <- plot_fig4(4, ggtit = "Fast-moving-distractors")
+
 gridExtra::grid.arrange(p1,p2, ncol = 2)
 
-ggsave("plots/Figure4_slow.png", p1, width = 6, height = 6)
-ggsave("plots/Figure4_fast.png", p2, width = 6, height = 6)
-ggsave("plots/Figure4_slow.eps", p1, width = 6, height = 6)
-ggsave("plots/Figure4_fast.eps", p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure4_slow.png"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure4_fast.png"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure4_slow.eps"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure4_fast.eps"), p2, width = 6, height = 6)
 ```
@@
 
-```{r exp 3 - statistics}
-df_exp2a %>% group_by(restk) %>% summarize(acc = mean(accuracy) * 100, sd = sd(accuracy) *100)
+```{r exp 2a - statistics}
+df_exp2a %>% 
+  group_by(restk) %>% 
+  summarize(acc = mean(accuracy) * 100, sd = sd(accuracy) * 100) %>% 
+  knitr::kable()
 ```
 
-Difference between symmetrical cases
-```{r}
-df_sym <- df_exp2a %>% filter((restk == 2 & type == 4) |(restk == 4 & type == 2))
-ez::ezANOVA(df_sym,
-        dv=accuracy,
+## Difference between symmetrical cases
+```{r exp 2a - symmetrical case, warning=F, message=F}
+
+df_exp2a %>% 
+  filter((restk == 2 & type == 4) |(restk == 4 & type == 2)) %>% 
+  ez::ezANOVA(
+        dv = accuracy,
         wid = subject,
-        within = restk)
-ez::ezStats(df_sym,
-        dv=accuracy,
+        within = restk, 
+        detailed = T) %>% 
+  apa::anova_apa()
+
+df_exp2a %>% 
+  filter((restk == 2 & type == 4) |(restk == 4 & type == 2)) %>%
+  ez::ezStats(
+        dv = accuracy,
         wid = subject,
@@
 
-Test with baseline
+## Test with baseline
 
@@
 
-```{r load data - exp 2b}
-load("../data/exp2_fin/responses/responses_171023.RData")
+```{r exp 2b - load data}
+df_exp2b <- readRDS(here::here("..", "data", "exp2b", "responses", "responses_171023.rds")) %>% 
+ filter(block != 0)
 
-df_exp2b <- filter(df, block != 0) 
 df_exp2b <- df_exp2b %>% mutate(restk = restk * 100, type = type * 100)
-rm(df)
 
-participants_exp4 <- read.csv("../data/exp2_fin/participants_171023.csv")
+participants_exp2b <- read.csv(here::here("..", "data", "exp2b", "participants_171023.csv"))
 
-df2_exp1bb <- rbind(df_exp2b, df_exp2b)
-df2_exp1bb$version <- 2
-df2_exp1bb$version[1:nrow(df_exp2b)] <- 1
+df2_exp2b <- rbind(df_exp2b, df_exp2b)
+df2_exp2b$version <- 2
+df2_exp2b$version[1:nrow(df_exp2b)] <- 1
 
@@
 tmp <- df_exp2b$restk
-df2_exp1bb$restk[df2_exp1bb$version == 2] <- df_exp2b$type
-df2_exp1bb$type[df2_exp1bb$version == 2] <- tmp
+df2_exp2b$restk[df2_exp2b$version == 2] <- df_exp2b$type
+df2_exp2b$type[df2_exp2b$version == 2] <- tmp
 
-df2_exp1bb$version <- factor(df2_exp1bb$version, labels = c("fix distractors' speed", "fix target's speed"))
+df2_exp2b$version <- factor(df2_exp2b$version, labels = c("fix distractors' speed", "fix target's speed"))
 ```
@@
 ## Participant info
-```{r exp4 - participants info}
-table(participants_exp4$gender)
-c(mean(participants_exp4$age), sd(participants_exp4$age)) %>% round(2)
+```{r exp2b - participants info}
+table(participants_exp2b$gender)
+c(mean(participants_exp2b$age), sd(participants_exp2b$age)) %>% round(2)
 ```
@@
 
-p_sp05 <- df2_exp1bb %>%
-  filter(restk == .5) %>%
-  ggplot(aes(x = type, y = accuracy, group = version)) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
-  geom_hline(yintercept=0.125) +
-  theme(aspect.ratio = 1) + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  theme(legend.position="none") +
-  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
-                     trans = "log2") + 
-  geom_vline(xintercept = .5, linetype = 2) +
-  ggtitle(expression("Fixed speed = 0.5"*degree*"/s"))
+p_sp05 <- plot_fig5(0.5)
+p_sp1 <- plot_fig5(1)
+p_sp2 <- plot_fig5(2)
+p_sp4 <- plot_fig5(4)
+p_sp8 <- plot_fig5(8)
+p_sp8_legend <- plot_fig5(8, show_legend = T)
 
-p_sp1 <- df2_exp1bb %>%
-  filter(restk == 1) %>%
-  ggplot(aes(x = type, y = accuracy, group = version)) + 
-  #facet_grid(~ restk) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
-  geom_hline(yintercept=0.125) +
-  theme(aspect.ratio = 1) + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  theme(legend.position="none") +
-  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
-                     trans = "log2") + 
-  geom_vline(xintercept = 1, linetype = 2) +
-  ggtitle(expression("Fixed speed = 1"*degree*"/s"))
-
-p_sp2 <- df2_exp1bb %>%
-  filter(restk == 2) %>%
-  ggplot(aes(x = type, y = accuracy, group = version)) + 
-  #facet_grid(~ restk) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
-  geom_hline(yintercept=0.125) +
-  theme(aspect.ratio = 1) + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  theme(legend.position="none") +
-  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
-                     trans = "log2") + 
-  geom_vline(xintercept = 2, linetype = 2) +
-  ggtitle(expression("Fixed speed = 2"*degree*"/s"))
-
-p_sp4 <- df2_exp1bb %>%
-  filter(restk == 4) %>%
-  ggplot(aes(x = type, y = accuracy, group = version)) + 
-  #facet_grid(~ restk) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
-  geom_hline(yintercept=0.125) +
-  theme(aspect.ratio = 1) + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  theme(legend.position="none") +
-  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
-                     trans = "log2") + 
-  geom_vline(xintercept = 4, linetype = 2) +
-  ggtitle(expression("Fixed speed = 4"*degree*"/s"))
-
-p_sp8 <- df2_exp1bb %>%
-  filter(restk == 8) %>%
-  ggplot(aes(x = type, y = accuracy, group = version)) + 
-  #facet_grid(~ restk) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
-  geom_hline(yintercept=0.125) +
-  theme(aspect.ratio = 1) + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  theme(legend.position="none") +
-  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
-                     trans = "log2") + 
-  geom_vline(xintercept = 8, linetype = 2) +
-  ggtitle(expression("Fixed speed = 8"*degree*"/s"))
-
-p_sp8_legend <- df2_exp1bb %>%
-  filter(restk == 8) %>%
-  ggplot(aes(x = type, y = accuracy, group = version)) + 
-  #facet_grid(~ restk) + 
-  stat_summary(fun.data = "mean_cl_boot") + 
-  stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
-  geom_hline(yintercept=0.125) +
-  theme(aspect.ratio = 1) + 
-  ylab("Accuracy") + 
-  ylim(0,1)+
-  scale_x_continuous("Speed of the others (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
-                     trans = "log2") + 
-  geom_vline(xintercept = 8, linetype = 2) +
-  ggtitle(expression("Fixed speed = 8"*degree*"/s"))
-
-gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 5)
-ggsave("plots/Fig5_sp05.eps", p_sp05, width = 6, height = 6)
-ggsave("plots/Fig5_sp1.eps", p_sp1, width = 6, height = 6)
-ggsave("plots/Fig5_sp2.eps", p_sp2, width = 6, height = 6)
-ggsave("plots/Fig5_sp4.eps", p_sp4, width = 6, height = 6)
-ggsave("plots/Fig5_sp8.eps", p_sp8, width = 6, height = 6)
-ggsave("plots/Fig5_sp8_legend.eps", p_sp8_legend, width = 6, height = 6)
+gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 3)
+ggsave(file.path(plot_pth, "Fig5_sp05.eps"), p_sp05, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5_sp1.eps"), p_sp1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5_sp2.eps"), p_sp2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5_sp4.eps"), p_sp4, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5_sp8.eps"), p_sp8, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5_sp8_legend.eps"), p_sp8_legend, width = 6, height = 6)
 # final plot was created in inkscape
@@
 
-```{r compute the assymetry, warning=F}
-df3_exp1bb <- df2_exp1bb %>% group_by(type, restk) %>% do(p=compute.p(.))
+```{r exp 2b - compute the assymetry, warning=F}
+df3_exp2b <- df2_exp2b %>% group_by(type, restk) %>% do(p=compute.p(.))
 
-df3_exp1bb$p <- unlist(df3_exp1bb$p) %>% round(3)
-df4_exp4 <- df2_exp1bb %>% group_by(type, restk) %>% do(ges=compute.des(.))
-df4_exp4$ges <- unlist(df4_exp4$ges) %>% round(2)
-df3_exp1bb$ges <- df4_exp4$ges
+df3_exp2b$p <- unlist(df3_exp2b$p) %>% round(3)
+df4_exp2b <- df2_exp2b %>% group_by(type, restk) %>% do(ges=compute.des(.))
+df4_exp2b$ges <- unlist(df4_exp2b$ges) %>% round(2)
+df3_exp2b$ges <- df4_exp2b$ges
 
-df5_exp4 <- df2_exp1bb %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
+df5_exp2b <- df2_exp2b %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
   group_by(type, restk) %>%
@@
 
-m <- matrix(df3_exp1bb$ges, nrow = 5)
+m <- matrix(df3_exp2b$ges, nrow = 5)
 rownames(m) <- levels(df_exp2b$type)
@@
 
-df3_exp1bb$ges <- as.vector(m)
+df3_exp2b$ges <- as.vector(m)
 
-m <- matrix(df3_exp1bb$p, nrow = 5)
+m <- matrix(df3_exp2b$p, nrow = 5)
 m[upper.tri(m, diag = T)] <- NA
-df3_exp1bb$p <- as.vector(m)
+df3_exp2b$p <- as.vector(m)
 
-m <- matrix(df5_exp4$acc_diff, nrow = 5)
+m <- matrix(df5_exp2b$acc_diff, nrow = 5)
 m[upper.tri(m, diag = T)] <- NA
-df3_exp1bb$acc_diff <- as.vector(m)
+df3_exp2b$acc_diff <- as.vector(m)
 
-df3_exp1bb$target_lower_than_dist <- df3_exp1bb$acc_diff < 0
-df3_exp1bb %>% filter(target_lower_than_dist)
+df3_exp2b$target_lower_than_dist <- df3_exp2b$acc_diff < 0
+df3_exp2b %>% filter(target_lower_than_dist) %>% knitr::kable()
 
-df3_exp1bb %>% filter(p < 0.05)
+df3_exp2b %>% filter(p < 0.05) %>% knitr::kable()
 
-differencies <- df3_exp1bb %>% filter(target_lower_than_dist)  %>% .$acc_diff *-1
+differencies <- df3_exp2b %>% filter(target_lower_than_dist)  %>% .$acc_diff *-1
 differencies %>% range() %>% round(2)

### 2018-07-03 R/tools.R
fix plot title

@@ -120,7 +120,7 @@ plot_fig4 <- function(restspd, ggtit) {
     ylim(0,1)+
     geom_vline(xintercept = restspd, linetype = 2) +
     scale_x_continuous("Target's speed (log scale)",breaks = c(0.5,1,2,3,4,6,8),labels = c("0.5","1","2","3","4","6","8"), trans = "log2") + 
-    ggtitle("Slow-moving-distractors")
+    ggtitle(ggtit)
 }
 
 plot_fig5 <- function(restspd, show_legend = F) {

### 2018-07-03 R/manuscript_app.Rmd
add anova tables

@@
 ## Participant info
-```{r}
+```{r exp1b - participant info}
 table(participants_exp1b$gender)
@@
 
-```{r plots experiment 2}
+```{r Figure 3}
 
@@
 
-```{r compute the assymetry - exp1b, warning=F}
+```{r exp 1b - compute the assymetry, warning=F}
 df3_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(p=compute.p(.))
@@
 
-```{r}
+```{r exp1b - test vs baseline}
 df_exp1b %>% 
@@
 
+## Table 1
+
+```{r exp 1b - Table 1}
+df_exp1b %>% 
+  filter(restk == 2) %>% 
+  ez::ezANOVA(dv = accuracy,
+        wid = subject,
+        within = type, 
+        detailed = T) %>% 
+  apa::anova_apa()
+
+df_exp1b %>% 
+  filter(restk == 4) %>% 
+  ez::ezANOVA(dv = accuracy,
+        wid = subject,
+        within = type, 
+        detailed = T) %>% 
+  apa::anova_apa()
+df_exp1b %>% 
+  filter(restk == 8) %>% 
+  ez::ezANOVA(dv = accuracy,
+        wid = subject,
+        within = type, 
+        detailed = T) %>% 
+  apa::anova_apa()
+
+df_exp1b %>% 
+  filter(restk == 16) %>% 
+  ez::ezANOVA(dv = accuracy,
+        wid = subject,
+        within = type, 
+        detailed = T) %>% 
+  apa::anova_apa()
+
+```
+
 # Experiment 2a
 
-```{r load data - exp 2a}
+```{r exp 2a - load data}
 df_exp2a <- readRDS(file.path(data_pth,"exp2a","responses","responses_150410.rds")) %>% 
@@
   mutate(restk = restk * 100, type = type * 100) %>% 
-  mutate(restk2 = recode(restk, `2` = "Slow-moving-distractors", `4` = "Fast-moving-distractors"))
+  mutate(restk2 = recode(restk, `2` = "Slow-moving-distractors", `4` = "Fast-moving-distractors")) %>% 
+  as_data_frame()
 
@@
 
-```{r exp2a - results accuracy}
-df_exp2a %>% 
-  group_by(restk) %>% 
-  summarize(accuracy_mean = mean(accuracy, na.rm = T)) %>% knitr::kable(digits = 2)
-```
+### Desciptive statistics
 
-## Figure 4
-
-```{r Figure 4}
-
-p1 <- plot_fig4(2, ggtit = "Slow-moving-distractors")
-
-p2 <- plot_fig4(4, ggtit = "Fast-moving-distractors")
-
-gridExtra::grid.arrange(p1,p2, ncol = 2)
-
-ggsave(file.path(plot_pth, "Figure4_slow.png"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure4_fast.png"), p2, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure4_slow.eps"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure4_fast.eps"), p2, width = 6, height = 6)
-```
-
-## Statistics
-
-```{r exp 2a - statistics}
+```{r exp 2a - descriptive statistics}
 df_exp2a %>% 
@@
   summarize(acc = mean(accuracy) * 100, sd = sd(accuracy) * 100) %>% 
-  knitr::kable()
+  knitr::kable(digits = 0)
+
+df_exp2a %>% 
+  filter(restk2 == "Slow-moving-distractors") %>% 
+  ez::ezStats(dv = accuracy,
+        wid = subject,
+        within = type)
+df_exp2a %>% 
+  filter(restk2 == "Fast-moving-distractors") %>% 
+  ez::ezStats(dv = accuracy,
+        wid = subject,
+        within = type)
+
 ```
 
-## Difference between symmetrical cases
+### Overall differences
+
+```{r exp 2a - overall differences, warning=F, message = F}
+df_exp2a %>% 
+  filter(restk2 == "Slow-moving-distractors") %>% 
+  ez::ezANOVA(dv = accuracy,
+        wid = subject,
+        within = type, 
+        detailed = T) %>% 
+  apa::anova_apa()
+
+df_exp2a %>% 
+  filter(restk2 == "Fast-moving-distractors") %>% 
+  ez::ezANOVA(dv = accuracy,
+        wid = as.factor(subject),
+        within = as.factor(type), 
+        detailed = T) %>% 
+  apa::anova_apa()
+```
+
+### Difference between symmetrical cases
 ```{r exp 2a - symmetrical case, warning=F, message=F}
@@
 
-## Test with baseline
+### Figure 4
+
+```{r Figure 4}
+
+p1 <- plot_fig4(2, ggtit = "Slow-moving-distractors")
+
+p2 <- plot_fig4(4, ggtit = "Fast-moving-distractors")
+
+gridExtra::grid.arrange(p1,p2, ncol = 2)
+
+ggsave(file.path(plot_pth, "Figure4_slow.png"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure4_fast.png"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure4_slow.eps"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure4_fast.eps"), p2, width = 6, height = 6)
+```
+
+### Test with baseline
 

### 2018-07-03 R/manuscript_app.Rmd
test anovas with factor
We were using linear predictor instead of categorical

@@
   apa::anova_apa()
+
+df_exp2a %>% 
+  filter(restk2 == "Slow-moving-distractors") %>% 
+  mutate(type2 = as.character(type)) %>% 
+  ez::ezANOVA(dv = accuracy,
+        wid = subject,
+        within = type2, 
+        detailed = T) %>% 
+  apa::anova_apa(sph_corr = "none")
+
+df_exp2a %>% 
+  filter(restk2 == "Fast-moving-distractors") %>% 
+  mutate(type2 = as.character(type)) %>% 
+  ez::ezANOVA(dv = accuracy,
+        wid = as.factor(subject),
+        within = as.factor(type2), 
+        detailed = T) %>% 
+  apa::anova_apa(sph_corr = "none")
 ```

### 2018-07-03 R/generate_vonmises_example.R
add von mises example
as one of the reviewers suggested, we could add some visualization of von mises ditribution

@@ -1,0 +1,42 @@
+
+# create data -------------------------------------------------------------
+set.seed(180307)
+
+library(tidyverse)
+
+if(!require(circular)) {install.packages("circular"); library(circular)}
+
+nDot  <- 100L
+t     <- 30
+kappa <- 16
+spd <- 1
+
+ang <- rvonmises(n, circular(0), kappa, control.circular=list(units="degrees"))
+
+y <- cos(ang)
+x <- sin(ang)
+
+df <- data_frame(id = 1:nDot, x, y, t = 1, ang)
+
+for(i in 1:t){
+  ang <- rvonmises(n,circular(0), kappa, control.circular=list(units="degrees"))
+
+  y <- cos(ang)
+  x <- sin(ang)
+  tmp <- data_frame(id = 1:nDot,x, y, t=i, ang)
+  df <- rbind(df, tmp)  
+}
+
+df2 <- df %>% 
+  group_by(id) %>% 
+  mutate(x = cumsum(x), y = cumsum(y)) %>% 
+  ungroup()
+
+df2 %>% 
+  filter(id < 6) %>% 
+  ggplot(aes(x,y, col = as.factor(id))) + 
+  geom_path() + 
+  theme(aspect.ratio = 1) +
+  xlim(-10,10)+
+  ylim(-10,10)
+

### 2018-07-03 R/generate_vonmises_example.R
another take on von mises generation

@@ -40,3 +40,43 @@ df2 %>%
   xlim(-10,10)+
   ylim(-10,10)
 
+
+# another take ------------------------------------------------------------
+
+nDot <- 10000
+
+ang_k16 <- rvonmises(nDot, circular(0), 16, control.circular=list(units="degrees"))
+h <- hist(as.numeric(ang_k16),plot = F, breaks = 0:360)
+h$counts
+data <- data_frame(
+  id = 1:360,
+  ang_bin = h$counts
+)
+
+# Make the plot
+p <- ggplot(data, aes(x=as.factor(id), y=ang_bin)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
+  
+  # This add the bars with a blue color
+  geom_bar(stat = "identity", fill = "black", width = 1) +
+coord_polar(start = 0) + 
+  scale_x_discrete(breaks = seq(0, 360), labels = seq(0, 360)) +
+  theme(
+    axis.text = element_blank()
+    
+  )
+  # Limits of the plot = very important. The negative value controls the size of the inner circle, the positive one is useful to add size over each bar
+  ylim(-100,120) +
+  
+  # Custom the theme: no axis title and no cartesian grid
+  theme_minimal() +
+  theme(
+    axis.text = element_blank(),
+    axis.title = element_blank(),
+    panel.grid = element_blank(),
+    plot.margin = unit(rep(-2,4), "cm")     # This remove unnecessary margin around plot
+  ) +
+  
+  # This makes the coordinate polar instead of cartesian.
+  coord_polar(start = 0)
+p
+

### 2018-07-16 R/generate_vonmises_example.R
bug fixes

@@ -6,12 +6,12 @@ library(tidyverse)
 
 if(!require(circular)) {install.packages("circular"); library(circular)}
 
-nDot  <- 100L
+nDot  <- 1000L
 t     <- 30
 kappa <- 16
 spd <- 1
 
-ang <- rvonmises(n, circular(0), kappa, control.circular=list(units="degrees"))
+ang <- rvonmises(nDot, circular(0), kappa, control.circular=list(units="degrees"))
 
 y <- cos(ang)
 x <- sin(ang)
@@ -19,7 +19,7 @@ x <- sin(ang)
 df <- data_frame(id = 1:nDot, x, y, t = 1, ang)
 
 for(i in 1:t){
-  ang <- rvonmises(n,circular(0), kappa, control.circular=list(units="degrees"))
+  ang <- rvonmises(nDot,circular(0), kappa, control.circular=list(units="degrees"))
 
   y <- cos(ang)
   x <- sin(ang)

### 2018-07-16 R/generate_vonmises_example.R
some more tries

@@ -1,5 +1,5 @@
 
-# create data -------------------------------------------------------------
+# von mises - circle -------------------------------------------------------------
 set.seed(180307)
 
 library(tidyverse)
@@ -7,20 +7,23 @@ library(tidyverse)
 if(!require(circular)) {install.packages("circular"); library(circular)}
 
 nDot  <- 1000L
-t     <- 30
+t     <- 15
 kappa <- 16
 spd <- 1
 
-ang <- rvonmises(nDot, circular(0), kappa, control.circular=list(units="degrees"))
-
+#angStarts <- circular(sample(0:360,nDot)) %>% conversion.circular()
+#ang <- sapply(angStarts, function(x) {rvonmises(1, x, kappa, control.circular=list(units="radians"))})
+ang <- rvonmises(nDot,circular(0), kappa, control.circular=list(units="radians"))
 y <- cos(ang)
 x <- sin(ang)
 
 df <- data_frame(id = 1:nDot, x, y, t = 1, ang)
 
 for(i in 1:t){
-  ang <- rvonmises(nDot,circular(0), kappa, control.circular=list(units="degrees"))
-
+  
+  
+  tmp <- rvonmises(nDot,circular(0), kappa, control.circular=list(units="radians"))
+  ang <- ang + tmp
   y <- cos(ang)
   x <- sin(ang)
   tmp <- data_frame(id = 1:nDot,x, y, t=i, ang)
@@ -33,13 +36,104 @@ df2 <- df %>%
   ungroup()
 
 df2 %>% 
+  group_by(id) %>% 
+  top_n(1,t) %>% 
+  ggplot(aes(x, y)) + 
+  geom_point(alpha = I(0.1)) + 
+  theme(aspect.ratio = 1) +
+  xlim(-30,30)+
+  ylim(-30,30)
+
+df2 %>% 
   filter(id < 6) %>% 
-  ggplot(aes(x,y, col = as.factor(id))) + 
+  ggplot(aes(x,y, col = as.factor(id))) +
+  geom_path() + 
+  theme(aspect.ratio = 1) +
+  xlim(-5,5)+
+  ylim(-5,5)
+
+
+# random initial direction ------------------------------------------------
+
+set.seed(180307)
+
+library(tidyverse)
+
+if(!require(circular)) {install.packages("circular"); library(circular)}
+
+nDot  <- 7L
[…]

### 2018-07-16 R/generate_vonmises_example.R
tools for paper

@@ -1,176 +1,59 @@
+rm(list = ls())
+
+source("tools.R")
 
 # von mises - circle -------------------------------------------------------------
 set.seed(180307)
 
 library(tidyverse)
+theme_set(theme_bw(16))
 
 if(!require(circular)) {install.packages("circular"); library(circular)}
 
 nDot  <- 1000L
 t     <- 15
-kappa <- 16
-spd <- 1
 
-#angStarts <- circular(sample(0:360,nDot)) %>% conversion.circular()
-#ang <- sapply(angStarts, function(x) {rvonmises(1, x, kappa, control.circular=list(units="radians"))})
-ang <- rvonmises(nDot,circular(0), kappa, control.circular=list(units="radians"))
-y <- cos(ang)
-x <- sin(ang)
+p1 <- create_data_scheme_vonmises(nDot, t, kappa = 2) %>% plot_vonmises_scheme(expression("Highly variable movement ("*kappa~"=2)"))
+p2 <- create_data_scheme_vonmises(nDot, t, kappa = 16) %>% plot_vonmises_scheme(expression("Medium variable movement ("*kappa~")=16"))
+p3 <- create_data_scheme_vonmises(nDot, t, kappa = 64) %>% plot_vonmises_scheme(expression("Low variable movement ("*kappa~")=64"))
+ggsave(here::here("..", "plots", "scheme_vonmises_k2.png"), p1, width = 6, height = 6)
+ggsave(here::here("..", "plots", "scheme_vonmises_k16.png"), p2, width = 6, height = 6)
+ggsave(here::here("..", "plots", "scheme_vonmises_k64.png"), p3, width = 6, height = 6)
 
-df <- data_frame(id = 1:nDot, x, y, t = 1, ang)
 
-for(i in 1:t){
+# real data ---------------------------------------------------------------
+
+data_pth <- here::here("..","data", "exp1b", "trajectories")
+
+traj_k64_raw <- read.table(file.path(data_pth, "T001_4_rest64.csv")) %>% 
+  as_data_frame() %>% 
+  mutate(t=1:n())
+
+trajx <- traj_k64_raw %>% 
+  select(V1,V3,V5,V7,V9,V11,V13,V15,t) %>% 
+  gather(key = "object", value = "xcoord", -t) %>% 
[…]

### 2018-07-16 R/tools.R

@@ -143,3 +143,45 @@ plot_fig5 <- function(restspd, show_legend = F) {
     p + theme(legend.position="none")
   }   
 }
+
+
+create_data_scheme_vonmises <- function(nDot, kappa, t) {
+  ang <- rvonmises(nDot,circular(0), kappa, control.circular=list(units="radians"))
+  
+  y <- cos(ang)
+  x <- sin(ang)
+  
+  df <- data_frame(id = 1:nDot, x, y, t = 1, ang)
+  
+  for(i in 1:t){
+    tmp <- rvonmises(nDot,circular(0), kappa, control.circular=list(units="radians"))
+    ang <- ang + tmp
+    y <- cos(ang)
+    x <- sin(ang)
+    tmp <- data_frame(id = 1:nDot,x, y, t=i, ang)
+    df <- rbind(df, tmp)  
+  }
+  
+  df2 <- df %>% 
+    group_by(id) %>% 
+    mutate(x = cumsum(x), y = cumsum(y)) %>% 
+    ungroup()
+  
+  return(df2)
+}
+plot_vonmises_scheme <- function(df, ggtit) {
+  df %>% 
+    group_by(id) %>% 
+    top_n(1,t) %>% 
+    ggplot(aes(x, y)) + 
+    geom_point(alpha = I(0.1)) + 
+    theme(aspect.ratio = 1) +
+    xlim(-30,30) +
+    ylim(-30,30) +
+    geom_segment(aes(x=0, xend=0, y=0, yend=8), 
+                   arrow = arrow(length = unit(0.5, "cm"), type = "closed"), size = 2, col = "red") +
+    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+    xlab("x [deg]") + 
+    ylab("y [deg]") + 
+    ggtitle(ggtit)
+}

### 2018-07-17 R/generate_vonmises_example.R
bug fix

@@ -14,8 +14,8 @@ nDot  <- 1000L
 t     <- 15
 
 p1 <- create_data_scheme_vonmises(nDot, t, kappa = 2) %>% plot_vonmises_scheme(expression("Highly variable movement ("*kappa~"=2)"))
-p2 <- create_data_scheme_vonmises(nDot, t, kappa = 16) %>% plot_vonmises_scheme(expression("Medium variable movement ("*kappa~")=16"))
-p3 <- create_data_scheme_vonmises(nDot, t, kappa = 64) %>% plot_vonmises_scheme(expression("Low variable movement ("*kappa~")=64"))
+p2 <- create_data_scheme_vonmises(nDot, t, kappa = 16) %>% plot_vonmises_scheme(expression("Medium variable movement ("*kappa~"=16)"))
+p3 <- create_data_scheme_vonmises(nDot, t, kappa = 64) %>% plot_vonmises_scheme(expression("Low variable movement ("*kappa~"=64)"))
 ggsave(here::here("..", "plots", "scheme_vonmises_k2.png"), p1, width = 6, height = 6)
 ggsave(here::here("..", "plots", "scheme_vonmises_k16.png"), p2, width = 6, height = 6)
 ggsave(here::here("..", "plots", "scheme_vonmises_k64.png"), p3, width = 6, height = 6)

### 2018-07-17 R/generate_vonmises_example.R
finalize new Figure

@@ -44,16 +44,21 @@ traj_k64 <- trajx %>%
   mutate(type = if_else(object == "o1", "target", "distractor"))
   
   
-traj_k64 %>% 
-  filter(t > 10) %>% 
-  ggplot(aes(xcoord, ycoord, linetype = type,group = object, col = object)) + 
-  geom_path(size = 1.5) + 
+p <- traj_k64 %>% 
+  filter(t > 10) %>%
+  filter(object %in% c("o1","o2","o7","o4","o5")) %>% 
+  ggplot(aes(xcoord, ycoord, group = object)) + 
+  geom_path(size = 0.5) + 
   theme(aspect.ratio = 1) + 
   xlim(-15,15) +
   ylim(-15,15) +
-  scale_linetype_manual(values=c("dotted", "solid")) + 
-  geom_point(data = traj_k64 %>% filter(t==1), aes(xcoord, ycoord, fill = type), size = 4, shape = 1, show.legend=FALSE) +
-  geom_point(data = traj_k64 %>% filter(t==max(t)), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
+  #scale_linetype_manual(values=c("solid", "solid")) + 
+  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o2","o7","o4","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
+  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o1")), aes(xcoord, ycoord, fill = type), size = 4, shape = 1, show.legend=FALSE) +
+  #geom_point(data = traj_k64 %>% filter(t==max(t),object %in% c("o1","o2","o7","o4","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
   guides(color = FALSE) +
   xlab("x [deg]") +
-  ylab("y [deg]")
+  ylab("y [deg]") +
+  ggtitle(expression("Target's "*kappa~"= 4; Distractors' "*kappa~"= 64"))
+
+ggsave(here::here("..", "plots", "scheme_trial_example.png"), p, width = 6, height = 6)

### 2018-07-17 R/manuscript_app_alt_clean.Rmd

---
title: "manuscript - APP"
author: "Filip Dechterenko"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

## Load libraries

```{r load libraries, warning=F, message=F, echo=FALSE}

if (!require(tidyverse)) {install.packages("tidyverse"); library(tidyverse)}
if (!require(ez)) {install.packages("ez"); library(ez)}
if (!require(psyphy)) {install.packages("psyphy"); library(psyphy)}

if (!require(here)) {install.packages("here")}

library(lme4)
library(lmerTest)

theme_set(theme_bw(16))
source("tools.R")
```

```{r echo=FALSE}
# Exp 1b
df_exp1b <- 
  readRDS(
    here::here("..", "data", "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk))
participants_exp1b <- 
  read.csv(file.path(data_pth, "exp1b", "participants_150526.csv"), fileEncoding = "UTF8")

# Exp 2b
df_exp2b <- 
  readRDS(
    here::here("..", "data", "exp2b", "responses", "responses_171023.rds")) %>% 
 filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_faster = (targetk > restk))
participants_exp2b <- 
  read.csv(here::here("..", "data", "exp2b", "participants_171023.csv"))
```

# Experiment 1b

```{r echo=F}
# accuracy summarised
accu_summary <- df_exp1b %>% 
  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
  group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
  dplyr::summarise(accu = mean(accuracy), n = n()) 
accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)

# duplicated values for contrast 0
accu_summaryx <- bind_rows(
  accu_summary,
  accu_summary %>% 
    filter(contrast_abs == 0, target_straight == F) %>% 
    mutate(target_straight = T)
)

# raw data with duplicated values for contrast 0
df_exp1bx <- bind_rows(
  df_exp1b,
  df_exp1b %>% 
    filter(contrast_abs == 0, target_straight == F) %>% 
    mutate(target_straight = T)
)
# yes no for psychophysics
d1b <- df_exp1b %>% 
  group_by(id, target_straight, contrast_abs) %>% 
  summarise(yes = sum(accuracy), no = n() - yes, accuracy = mean(accuracy))
d1bx <- bind_rows(
  d1b,
  d1b %>% 
    filter(contrast_abs == 0) %>% ungroup() %>% mutate(target_straight = T)
)
```

```{r Charts1b}
accu_summary %>% 
  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
  geom_jitter() 
accu_summary %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_straight, colour = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5)
```

## Individual data
```{r}
d1bx %>% ggplot(aes(x = contrast_abs, y = accuracy, colour = target_straight)) +
  geom_point(alpha = .5) + facet_wrap(~id)
```

## ANOVA

### Linear 
```{r}
# linear
ezANOVA(accu_summaryx,
        accu, id, within = .(contrast_abs, target_straight))
```

### As factor
```{r}
# as factor and without contrast==0
ezANOVA(accu_summary_wo_0,
        accu, id, within = .(contrast_abs_f, target_straight))
```

## Mixed models

### Analysis as factors

```{r}
# as factor
m0 <- lmer(accu ~ (1|id), 
           data = accu_summary_wo_0)
summary(m0)
m1 <- lmer(accu ~ contrast_abs_f + (1|id), 
           data = accu_summary_wo_0)
summary(m1)
m2 <- lmer(accu ~ contrast_abs_f + target_straight + (1|id), 
           data = accu_summary_wo_0)
summary(m2)
m3 <- lmer(accu ~ contrast_abs_f * target_straight + (1|id), 
           data = accu_summary_wo_0)
summary(m3)
m4 <- lmer(accu ~ contrast_abs_f + contrast_abs_f:target_straight + (1|id), 
           data = accu_summary_wo_0)
```

### Linear

```{r}
m0 <- lmer(accu ~ (contrast_abs|id), data = accu_summaryx)
summary(m0)
m1 <- lmer(accu ~ contrast_abs + (contrast_abs|id), data = accu_summaryx)
summary(m1)
m2 <- lmer(accu ~ contrast_abs + target_straight + (contrast_abs|id), data = accu_summaryx)
summary(m2)
m3 <- lmer(accu ~ contrast_abs * target_straight + (1|id), data = accu_summaryx)
summary(m3)
m4 <- lmer(accu ~ contrast_abs + contrast_abs:target_straight + (1|id), data = accu_summaryx)
summary(m4)

```

### Logistic
```{r}
m0 <- glmer(accuracy ~ (1|id), 
            data = df_exp1bx, family = binomial())
summary(m0)
m1 <- glmer(accuracy ~ contrast_abs + (1|id), 
            data = df_exp1bx, family = binomial())
summary(m1)
m2 <- glmer(accuracy ~ contrast_abs + target_straight + (1|id), 
            data = df_exp1bx, family = binomial())
summary(m2)
m3 <- glmer(accuracy ~ contrast_abs * target_straight + (1|id), 
            data = df_exp1bx, family = binomial())
summary(m3)

```

### Psychophysics

```{r}
df.pf <- df_exp1bx %>% 
  group_by(contrast_abs, target_straight) %>% 
  summarise(yes = sum(accuracy), no = n() - sum(accuracy), 
            accuracy = 1 - mean(accuracy))

pf_ts <- psyfun.2asym(cbind(yes, no) ~ contrast_abs, 
                      data = df.pf %>% filter(target_straight), 
                      link = weib.2asym, init.g = 0.125, init.lam = 0.05 )
pf_tb <- psyfun.2asym(cbind(yes, no) ~ contrast_abs, 
                      data = df.pf %>% filter(!target_straight), 
                      link = weib.2asym, init.g = 0.125, init.lam = 0.05 )

x <- seq(0, 6,0.01)
ys <- predict(pf_ts, data.frame(contrast_abs = x), type = "response")
yb <- predict(pf_tb, data.frame(contrast_abs = x), type = "response")

dfmodel <- data.frame(x, y = c(ys, yb), 
                      target_straight = rep(c(T,F), each = length(x)))

p <- ggplot(data = dfmodel, aes(x = x, y = y, colour = target_straight)) + 
  geom_line(size = 1.5) + 
  stat_summary(data = df.pf, aes(x = contrast_abs, y = accuracy), 
               fun.data = "mean_cl_boot", size = 1) +
  NULL
p

summary(pf_ts)
summary(pf_tb)
```

# Experiment 2b

```{r echo=F}
# accuracy summarised
accu_summary <- df_exp2b %>% 
  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
  group_by(id, contrast_abs, contrast_abs_f, target_faster) %>% 
  dplyr::summarise(accu = mean(accuracy), n = n()) 
accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)

# duplicated values for contrast 0
accu_summaryx <- bind_rows(
  accu_summary,
  accu_summary %>% 
    filter(contrast_abs == 0, target_faster == F) %>% 
    mutate(target_faster = T)
)

# raw data with duplicated values for contrast 0
df_exp2bx <- bind_rows(
  df_exp2b,
  df_exp2b %>% 
    filter(contrast_abs == 0, target_faster == F) %>% 
    mutate(target_faster = T)
)
# yes no for psychophysics
d2b <- df_exp2b %>% 
  group_by(id, target_faster, contrast_abs) %>% 
  summarise(yes = sum(accuracy), no = n() - yes, accuracy = mean(accuracy))
d2bx <- bind_rows(
  d2b,
  d2b %>% 
    filter(contrast_abs == 0) %>% ungroup() %>% mutate(target_faster = T)
)
```

```{r Charts2b}
accu_summary %>% 
  ggplot(aes(x = contrast_abs, y = accu, colour = target_faster)) + 
  geom_jitter() 
accu_summary %>% 
  ggplot(
    aes(x = contrast_abs, y = accu, 
        group = target_faster, colour = target_faster)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5)
```

## Individual data
```{r}
d2bx %>% ggplot(aes(x = contrast_abs, y = accuracy, colour = target_faster)) +
  geom_point(alpha = .5) + facet_wrap(~id)
weird_performance <- c(1, 5, 14)
```

## ANOVA

### Linear 
```{r}
# linear
ezANOVA(accu_summaryx,
        accu, id, within = .(contrast_abs, target_faster))
```

### As factor
```{r}
# as factor and without contrast==0
ezANOVA(accu_summary_wo_0,
        accu, id, within = .(contrast_abs_f, target_faster))
```

### Test without weird performance
```{r}
# linear
ezANOVA(accu_summaryx %>% filter(!id %in% weird_performance),
        accu, id, within = .(contrast_abs, target_faster))
# as factor and without contrast==0
ezANOVA(accu_summary_wo_0 %>% filter(!id %in% weird_performance),
        accu, id, within = .(contrast_abs_f, target_faster))
```

## Mixed models

### Analysis as factors

```{r}
# as factor
m0 <- lmer(accu ~ (1|id), 
           data = accu_summary_wo_0)
summary(m0)
m1 <- lmer(accu ~ contrast_abs_f + (1|id), 
           data = accu_summary_wo_0)
summary(m1)
m2 <- lmer(accu ~ contrast_abs_f + target_faster + (1|id), 
           data = accu_summary_wo_0)
summary(m2)
m3 <- lmer(accu ~ contrast_abs_f * target_faster + (1|id), 
           data = accu_summary_wo_0)
summary(m3)
m4 <- lmer(accu ~ contrast_abs_f + contrast_abs_f:target_faster + (1|id), 
           data = accu_summary_wo_0)
```

### Linear

```{r}
m0 <- lmer(accu ~ (contrast_abs|id), data = accu_summaryx)
summary(m0)
m1 <- lmer(accu ~ contrast_abs + (contrast_abs|id), data = accu_summaryx)
summary(m1)
m2 <- lmer(accu ~ contrast_abs + target_faster + (contrast_abs|id), data = accu_summaryx)
summary(m2)
m3 <- lmer(accu ~ contrast_abs * target_faster + (1|id), data = accu_summaryx)
summary(m3)
m4 <- lmer(accu ~ contrast_abs + contrast_abs:target_faster + (1|id), data = accu_summaryx)
summary(m4)

```

### Logistic
```{r}
m0 <- glmer(accuracy ~ (1|id), 
            data = df_exp2bx, family = binomial())
summary(m0)
m1 <- glmer(accuracy ~ contrast_abs + (1|id), 
            data = df_exp2bx, family = binomial())
summary(m1)
m2 <- glmer(accuracy ~ contrast_abs + target_faster + (1|id), 
            data = df_exp2bx, family = binomial())
summary(m2)
m3 <- glmer(accuracy ~ contrast_abs * target_faster + (1|id), 
            data = df_exp2bx, family = binomial())
summary(m3)
```

### Test w/o weird performance in logistic regression
```{r}
m0 <- glmer(accuracy ~ (1|id), 
            data = df_exp2bx %>% filter(!id %in% weird_performance), family = binomial())
summary(m0)
m3 <- glmer(accuracy ~ contrast_abs * target_faster + (1|id), 
            data = df_exp2bx %>% filter(!id %in% weird_performance), family = binomial())
summary(m3)
anova(m3,m0)
```

### Psychophysics

```{r}
df.pf <- df_exp2bx %>% 
  group_by(contrast_abs, target_faster) %>% 
  summarise(yes = sum(accuracy), no = n() - sum(accuracy), 
            accuracy = 1 - mean(accuracy))

pf_ts <- psyfun.2asym(cbind(yes, no) ~ contrast_abs, 
                      data = df.pf %>% filter(target_faster), 
                      link = weib.2asym, init.g = 0.125, init.lam = 0.05)
pf_tb <- psyfun.2asym(cbind(yes, no) ~ contrast_abs, 
                      data = df.pf %>% filter(!target_faster), 
                      link = weib.2asym, init.g = 0.125, init.lam = 0.05)

x <- seq(0, 6,0.01)
ys <- predict(pf_ts, data.frame(contrast_abs = x), type = "response")
yb <- predict(pf_tb, data.frame(contrast_abs = x), type = "response")

dfmodel <- data.frame(x, y = c(ys, yb), 
                      target_faster = rep(c(T,F), each = length(x)))

p <- ggplot(data = dfmodel, aes(x = x, y = y, colour = target_faster)) + 
  geom_line(size = 1.5) + 
  stat_summary(data = df.pf, aes(x = contrast_abs, y = accuracy), 
               fun.data = "mean_cl_boot", size = 1) +
  NULL
p

summary(pf_ts)
summary(pf_tb)
```

### 2018-07-19 R/manuscript_app_alt_clean.Rmd
new code

@@
 source("tools.R")
+
+data_pth <- here::here("..", "data")
 ```
@@
   readRDS(
-    here::here("..", "data", "exp1b", "responses", "responses_150622.rds")) %>% 
+    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
   filter(block != 0) %>% as_tibble(.) %>% 
@@
   readRDS(
-    here::here("..", "data", "exp2b", "responses", "responses_171023.rds")) %>% 
+    file.path(data_pth, "exp2b", "responses", "responses_171023.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
@@
 participants_exp2b <- 
-  read.csv(here::here("..", "data", "exp2b", "participants_171023.csv"))
+  read.csv(file.path(data_pth, "exp2b", "participants_171023.csv"))
 ```
@@
 
+## Individual data
+```{r}
+d1bx %>% ggplot(aes(x = contrast_abs, y = accuracy, colour = target_straight)) +
+  geom_point(alpha = .5) + facet_wrap(~id)
+```
+
 ```{r Charts1b}
+#accu_summary %>% 
+#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
+#  geom_jitter() 
+accu_summaryx %>% 
+  ggplot(
+    aes(x = contrast_abs, y = accu, 
+        group = target_straight, shape = target_straight, linetype = target_straight)) + 
+  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
+  stat_summary(fun.y = "mean", alpha = .5, geom = "line") +
+
+  theme(aspect.ratio = 1) + 
+  xlab("c") + ylab("Accuracy")
+```
+
+```{r Charts1b without one participant}
 accu_summary %>% 
+  filter(id!= 13)
   ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
@@
   stat_summary(fun.data = "mean_cl_boot", alpha = .5)
-```
-
-## Individual data
-```{r}
-d1bx %>% ggplot(aes(x = contrast_abs, y = accuracy, colour = target_straight)) +
-  geom_point(alpha = .5) + facet_wrap(~id)
 ```
@@
 ezANOVA(accu_summary_wo_0,
-        accu, id, within = .(contrast_abs_f, target_straight))
+        accu, id, within = .(contrast_abs_f, target_straight),detailed = T)$ANOVA %>% 
+  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
+         partial_eta = (SSn/(SSn+SSd)) %>% round(2))
+
+```
+
+### Post hoc tests
+
+```{r}
+(accu_summary_wo_0 %>% 
+  filter(contrast_abs_f == 1) %>% 
+ezANOVA(accu, id, within = .(target_straight),detailed = T))$ANOVA %>% 
+  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
+         partial_eta = (SSn/(SSn+SSd)) %>% round(2))
+
+(accu_summary_wo_0 %>% 
+  filter(contrast_abs_f == 2) %>% 
+ezANOVA(accu, id, within = .(target_straight),detailed = T))$ANOVA %>% 
+  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
+         partial_eta = (SSn/(SSn+SSd)) %>% round(2))
+
+(accu_summary_wo_0 %>% 
+  filter(contrast_abs_f == 3) %>% 
+ezANOVA(accu, id, within = .(target_straight),detailed = T))$ANOVA %>% 
+  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
+         partial_eta = (SSn/(SSn+SSd)) %>% round(2))
+
+(accu_summary_wo_0 %>% 
+  filter(contrast_abs_f == 4) %>% 
+ezANOVA(accu, id, within = .(target_straight),detailed = T))$ANOVA %>% 
+  mutate(F = round(F,2), p = round(p,3),ges = round(ges,2),
+         partial_eta = (SSn/(SSn+SSd)) %>% round(2))
+
 ```
@@
 
+## Individual data
+```{r}
+d2bx %>% ggplot(aes(x = contrast_abs, y = accuracy, colour = target_faster)) +
+  geom_point(alpha = .5) + facet_wrap(~id)
+weird_performance <- c(1, 5, 14)
+```
+
 ```{r Charts2b}
@@
 
-## Individual data
-```{r}
-d2bx %>% ggplot(aes(x = contrast_abs, y = accuracy, colour = target_faster)) +
-  geom_point(alpha = .5) + facet_wrap(~id)
-weird_performance <- c(1, 5, 14)
+```{r Charts2b without weird}
+accu_summary %>% 
+  filter(!id %in% weird_performance) %>% 
+  ggplot(
+    aes(x = contrast_abs, y = accu, 
+        group = target_faster, colour = target_faster)) + 
+  stat_summary(fun.data = "mean_cl_boot", alpha = .5)
 ```

### 2018-07-20 R/tools.R
add kl distance

@@ -185,3 +185,11 @@ plot_vonmises_scheme <- function(df, ggtit) {
     ylab("y [deg]") + 
     ggtitle(ggtit)
 }
+
+kl_distance <- function(k1, k2) {
+  x <- seq(from = -pi, to = pi, length.out = 1000)
+  p_k1 <- dvonmises(x,mu = circular(0), kappa = k1)
+  p_k2 <- dvonmises(x,mu = circular(0), kappa = k2)
+  m <- spatialEco::kl.divergence(cbind(p_k1,p_k2))
+  (m[1,2]+m[2,1]) / 2
+}

### 2018-07-21 R/manuscript_app_alt_clean.Rmd
add kl distance
new ratio

@@
   mutate(contrast_abs = abs(log2(targetk / restk)), 
-         target_straight = (targetk > restk))
+         target_straight = (targetk > restk),
+         ratio = (besselI(targetk,0) * exp(targetk)) / (besselI(restk,0) * exp(restk)),
+         ratio_abs = abs(log((besselI(targetk,0) * exp(targetk))) / (besselI(restk,0) * exp(restk))))
 participants_exp1b <- 
@@
 
+```{r kl distance}
+
+ks <- c(2,4,8,16,64)
+n <- length(ks)
+
+m <- matrix(rep(0,n*n), ncol = n)
+source("tools.R")
+for (i in 1:length(ks)) {
+  for (j in i:length(ks)) {
+    m[i,j] <- kl_distance(ks[i],ks[j])    
+  } 
+}
+rownames(m) <- colnames(m) <- ks
+
+df_kl <- as_data_frame(m) %>%
+  mutate(k1 = rownames(m)) %>% 
+  gather(k2, value = kl_distance,-k1) %>% 
+  mutate(k1 = as.numeric(k1), k2 = as.numeric(k2)) %>% 
+  filter(k2>=k1) %>% 
+  distinct()
+
+df_kl <- df_kl %>% bind_rows(df_kl %>% mutate(tmp =k1, k1=k2,k2=tmp) %>% select(-tmp))
+
+df_exp1b <- df_exp1b %>% 
+  left_join(df_kl, by = c("targetk"="k1","restk"="k2"))
+```
+
 # Experiment 1b
@@
   mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
-  group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
-  dplyr::summarise(accu = mean(accuracy), n = n()) 
+  group_by(id, contrast_abs, contrast_abs_f, target_straight, kl_distance,ratio,ratio_abs) %>% 
+  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
+  ungroup()
 accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)
@@
   xlab("c") + ylab("Accuracy")
+```
+
+```{r Charts1b kl distance}
+#accu_summary %>% 
+#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
+#  geom_jitter() 
+accu_summaryx %>% 
+  ggplot(
+    aes(x = kl_distance, y = accu, 
+        group = target_straight, shape = target_straight, linetype = target_straight)) + 
+  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
+  stat_summary(fun.y = "mean", alpha = .5, geom = "line") +
+
+  theme(aspect.ratio = 1) + 
+  xlab("kl distance") + ylab("Accuracy")
+```
+
+```{r Charts1b ratio}
+#accu_summary %>% 
+#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
+#  geom_jitter() 
+accu_summaryx %>% 
+  ggplot(
+    aes(x = ratio, y = accu, 
+        group = target_straight, shape = target_straight, linetype = target_straight)) + 
+  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
+  stat_summary(fun.y = "mean", alpha = .5, geom = "line") +
+
+  theme(aspect.ratio = 1) + 
+  xlab("kl distance") + ylab("Accuracy") +scale_x_log10()
+```
+
+```{r Charts1b ratio abs}
+#accu_summary %>% 
+#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
+#  geom_jitter() 
+accu_summaryx %>% 
+  ggplot(
+    aes(x = ratio_abs, y = accu, 
+        group = target_straight, shape = target_straight, linetype = target_straight)) + 
+  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
+  stat_summary(fun.y = "mean", alpha = .5, geom = "line") +
+
+  theme(aspect.ratio = 1) + 
+  xlab("kl distance") + ylab("Accuracy") +scale_x_continuous(trans ="log")
 ```

### 2018-07-21 R/tools.R

@@ -188,8 +188,8 @@ plot_vonmises_scheme <- function(df, ggtit) {
 
 kl_distance <- function(k1, k2) {
   x <- seq(from = -pi, to = pi, length.out = 1000)
-  p_k1 <- dvonmises(x,mu = circular(0), kappa = k1)
-  p_k2 <- dvonmises(x,mu = circular(0), kappa = k2)
+  p_k1 <- circular::dvonmises(x,mu = circular::circular(0), kappa = k1)
+  p_k2 <- circular::dvonmises(x,mu = circular::circular(0), kappa = k2)
   m <- spatialEco::kl.divergence(cbind(p_k1,p_k2))
   (m[1,2]+m[2,1]) / 2
 }

### 2018-08-08 R/manuscript_app_alt_clean.Rmd
fix ratio function error

@@
          target_straight = (targetk > restk),
-         ratio = (besselI(targetk,0) * exp(targetk)) / (besselI(restk,0) * exp(restk)),
-         ratio_abs = abs(log((besselI(targetk,0) * exp(targetk))) / (besselI(restk,0) * exp(restk))))
+         ratio = (besselI(restk,0) * exp(targetk)) / (besselI(targetk,0) * exp(restk)),
+         ratio_abs = abs(log((besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))),
+         ratio_abs = abs(log(
+           (besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))))
 participants_exp1b <- 
@@
   theme(aspect.ratio = 1) + 
-  xlab("kl distance") + ylab("Accuracy") +scale_x_continuous(trans ="log")
+  xlab("ratio") + ylab("Accuracy") +scale_x_continuous(trans ="log")
 ```

### 2018-09-24 R/tools.R
center von mises scheme

@@ -183,7 +183,8 @@ plot_vonmises_scheme <- function(df, ggtit) {
     theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
     xlab("x [deg]") + 
     ylab("y [deg]") + 
-    ggtitle(ggtit)
+    ggtitle(ggtit) + 
+    theme(plot.title = element_text(hjust = 0.5))
 }
 
 kl_distance <- function(k1, k2) {

### 2018-09-24 R/generate_vonmises_example.R
center heading and first attempt to make video

@@ -1,5 +1,7 @@
 rm(list = ls())
 
+library(tidyverse)
+
 source("tools.R")
 
 # von mises - circle -------------------------------------------------------------
@@ -46,19 +48,43 @@ traj_k64 <- trajx %>%
   
 p <- traj_k64 %>% 
   filter(t > 10) %>%
-  filter(object %in% c("o1","o2","o7","o4","o5")) %>% 
+  filter(object %in% c("o1","o2","o7","o3","o5")) %>% 
   ggplot(aes(xcoord, ycoord, group = object)) + 
   geom_path(size = 0.5) + 
   theme(aspect.ratio = 1) + 
   xlim(-15,15) +
   ylim(-15,15) +
   #scale_linetype_manual(values=c("solid", "solid")) + 
-  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o2","o7","o4","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
+  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o2","o7","o3","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
   geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o1")), aes(xcoord, ycoord, fill = type), size = 4, shape = 1, show.legend=FALSE) +
   #geom_point(data = traj_k64 %>% filter(t==max(t),object %in% c("o1","o2","o7","o4","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
   guides(color = FALSE) +
   xlab("x [deg]") +
   ylab("y [deg]") +
-  ggtitle(expression("Target's "*kappa~"= 4; Distractors' "*kappa~"= 64"))
-
+  ggtitle(expression("Target's "*kappa~"= 4; Distractors' "*kappa~"= 64")) +
+  theme(plot.title = element_text(hjust = 0.5))
+p
 ggsave(here::here("..", "plots", "scheme_trial_example.png"), p, width = 6, height = 6)
+
+
+# video -------------------------------------------------------------------
+library(gganimate)
+theme_set(theme_bw(16))
+
+p <- traj_k64 %>% 
+  ggplot(aes(xcoord, ycoord, group = object)) + 
+  geom_point(size = 4) + 
[…]

### 2018-09-24 R/manuscript_app.Rmd
remove fitting by weibull

@@
 ggsave(file.path(plot_pth, "Figure2_ballistic.eps"), p2, width = 6, height = 6)
-```
-
-```{r exp1a - fitting weibull}
-
-df.pf <- df_exp1a %>% 
-  filter(restk2 == "Ballistic-like", type %in% c(2,4,8,16,32))
-
-df.pf2 <- df.pf %>% 
-  group_by(type) %>% 
-  summarise(yes = sum(accuracy), no = n() - sum(accuracy), accuracy = 1 - mean(accuracy))
-
-pf <- psyfun.2asym(cbind(yes, no) ~ type, data = df.pf2, link = weib.2asym, init.g = 0.125, init.lam = 0.05 )
-
-x <- seq(-2,32,0.01)
-y <- predict(pf, data.frame(type = x), type="response")
-
-dfmodel <- data.frame(x, y)
-
-p <- ggplot(data = dfmodel, aes(x = x, y = y)) + geom_line(color="red", size =1.5) + stat_summary(data = df.pf, aes(x = type, y=accuracy),fun.data = "mean_cl_boot", size = 1) + scale_x_continuous(expression("Target's"~kappa), breaks = df.pf2$type) + ylab("Accuracy")
-p
-
 ```

### 2018-09-24 R/tools.R
center title

@@ -78,9 +78,10 @@ plot_fig2 <- function(restk_var, ggtit) {
     theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
     ylab("Accuracy") + 
     ylim(0,1)+
-    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,8,16,32,64,128),labels = c("1","8","16","32","64","128"), trans = "log2") + 
+    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,2,4,8,16,32,64,128),labels = c("1","2","4","8","16","32","64","128"), trans = "log2") + 
     geom_vline(xintercept = restk_var, linetype = 2) +
-    ggtitle(ggtit)
+    ggtitle(ggtit) +
+    theme(plot.title = element_text(hjust = 0.5))
 }
 
 plot_fig3 <- function(restk_var, show_legend = F) {
@@ -98,7 +99,8 @@ plot_fig3 <- function(restk_var, show_legend = F) {
     scale_x_continuous(expression("Variable"~kappa~" (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
     scale_linetype_manual(values = c(2,1)) +
     geom_vline(xintercept = restk_var, linetype = 2) +
-    ggtitle(bquote("Fixed "~kappa~"= "~.(restk_var)))
+    ggtitle(bquote("Fixed "~kappa~"= "~.(restk_var))) +
+    theme(plot.title = element_text(hjust = 0.5))
   
   if (show_legend) {
     p 

### 2018-09-25 R/manuscript_app.Rmd
changes according the paper changes

@@
 ```{r exp1b  - load data}
-df_exp1b <- readRDS(file.path(data_pth,"exp1b","responses","responses_150622.rds")) %>% 
+#df_exp1b <- readRDS(file.path(data_pth,"exp1b","responses","responses_150622.rds")) %>% 
   filter(block != 0)
@@
 
-df2_exp1b <- rbind(df_exp1b,df_exp1b)
-df2_exp1b$version <- 2
-df2_exp1b$version[1:nrow(df_exp1b)] <- 1
+#df2_exp1b <- rbind(df_exp1b,df_exp1b)
+#df2_exp1b$version <- 2
+#df2_exp1b$version[1:nrow(df_exp1b)] <- 1
 
 # this is a little hack, just to make a correct ggplot with one line
-tmp <- df_exp1b$restk
-df2_exp1b$restk[df2_exp1b$version == 2] <- df_exp1b$type
-df2_exp1b$type[df2_exp1b$version == 2] <- tmp
+#tmp <- df_exp1b$restk
+#df2_exp1b$restk[df2_exp1b$version == 2] <- df_exp1b$type
+#df2_exp1b$type[df2_exp1b$version == 2] <- tmp
 
-df2_exp1b$version <- factor(df2_exp1b$version, labels = c("fix distractors' k", "fix target's k"))
+#df2_exp1b$version <- factor(df2_exp1b$version, labels = c("fix distractors' k", "fix target's k"))
+
+df_exp1b <- 
+  readRDS(
+    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
+  filter(block != 0) %>% as_tibble(.) %>% 
+  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
+  mutate(contrast_abs = abs(log2(targetk / restk)), 
+         target_straight = (targetk > restk),
+         ratio = (besselI(restk,0) * exp(targetk)) / (besselI(targetk,0) * exp(restk)),
+         ratio_abs = abs(log((besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))),
+         ratio_abs = abs(log(
+           (besselI(restk,0) * exp(targetk))) / (besselI(targetk,0) * exp(restk))))
 ```
@@
 ```{r Figure 3}
+accu_summary <- df_exp1b %>% 
+  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
+  group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
+  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
+  ungroup()
+accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)
 
-p_k2 <- plot_fig3(2)
-p_k4 <- plot_fig3(4)
-p_k8 <- plot_fig3(8)
-p_k16 <- plot_fig3(16)
-p_k64 <- plot_fig3(64)
-p_k64_legend <- plot_fig3(64, show_legend = T)
+# duplicated values for contrast 0
+accu_summaryx <- bind_rows(
+  accu_summary,
+  accu_summary %>% 
+    filter(contrast_abs == 0, target_straight == F) %>% 
+    mutate(target_straight = T)
+)
 
-gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
-ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
-# final plot was created in inkscape
+p <- accu_summaryx %>% 
+  ggplot(
+    aes(x = contrast_abs, y = accu, 
+        group = target_straight, shape = target_straight, linetype = target_straight)) + 
+  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
+  stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
+  theme(aspect.ratio = 1) + 
+  scale_shape_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
+  scale_linetype_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
+  xlab("contrast") + ylab("Accuracy")
+ggsave(file.path(plot_pth, "Figure3.png"), p, width = 9, height = 6)
 ```
@@
 
-We run multiple within subject aova
+We run multiple within subject anova
 
@@
 ```
+
+# Appendix
+
+```{r}
+#p_k2 <- plot_fig3(2)
+#p_k4 <- plot_fig3(4)
+#p_k8 <- plot_fig3(8)
+#p_k16 <- plot_fig3(16)
+#p_k64 <- plot_fig3(64)
+#p_k64_legend <- plot_fig3(64, show_legend = T)
+
+#gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
+#ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
+#ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
+#ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
+#ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
+#ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
+#ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
+# final plot was created in inkscape
+```

### 2018-09-25 R/manuscript_app_alt_clean.Rmd
change axis description
changes according the paper changes

@@
   stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
-
   theme(aspect.ratio = 1) + 
-  xlab("c") + ylab("Accuracy")
+  scale_shape_discrete("Target straighter") + 
+  xlab("contrast") + ylab("Accuracy")
 ```
@@
   theme(aspect.ratio = 1) + 
-  xlab("kl distance") + ylab("Accuracy") +scale_x_log10()
+  xlab("PDF ratio") + ylab("Accuracy") +scale_x_log10()
 ```

### 2018-09-25 R/manuscript_app.Rmd
new Figure 3b

@@
 }
+
 ```
@@
 #df_exp1b <- readRDS(file.path(data_pth,"exp1b","responses","responses_150622.rds")) %>% 
-  filter(block != 0)
+#  filter(block != 0)
 
@@
 
-## Figure 3
+## Figure 3a
 
-```{r Figure 3}
+```{r Figure 3a}
+df_exp1b %>% 
+  ggplot(aes(x = targetk, y = accuracy) + 
+    facet_grid(~restk, 
+               labeller = labeller(
+        xfacet = c(`2` = expression("Target's"~kappa~"=2"), 
+                   `4` = expression("Target's"~kappa~"=4"),
+                   `8` = expression("Target's"~kappa~"=8"),
+                   `16` = expression("Target's"~kappa~"=16"),
+                   `64` = expression("Target's"~kappa~"=64"))
+
+    )) +
+    stat_summary(fun.data = "mean_cl_boot") + 
+    stat_summary(fun.y = mean, geom = "line") + 
+    geom_hline(yintercept=0.125) + 
+    theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
+    ylab("Accuracy") + 
+    ylim(0,1)+
+    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,2,4,8,16,32,64,128),labels = c("1","2","4","8","16","32","64","128"), trans = "log2") + 
+    geom_vline(xintercept = restk_var, linetype = 2) +
+    ggtitle(ggtit) +
+    theme(plot.title = element_text(hjust = 0.5))
+```
+
+## Figure 3b
+
+```{r Figure 3b}
 accu_summary <- df_exp1b %>% 
@@
   xlab("contrast") + ylab("Accuracy")
+p
 ggsave(file.path(plot_pth, "Figure3.png"), p, width = 9, height = 6)

### 2018-09-25 R/tools.R

@@ -110,6 +110,26 @@ plot_fig3 <- function(restk_var, show_legend = F) {
   
 }
 
+plot_fig3b <- function() {
+  restk_lab <- as_labeller(c(`2` = expression("Distractor's"~kappa~"=2"), 
+                             `4` = expression("Distractor's"~kappa~"=4"),
+                             `8` = expression("Distractor's"~kappa~"=8"),
+                             `16` = expression("Distractor's"~kappa~"=16"),
+                             `64` = expression("Distractor's"~kappa~"=64")), label_parsed)
+  p <- df_exp1b %>% 
+    ggplot(aes(x = targetk, y = accuracy)) + 
+    facet_grid(~restk, labeller = restk_lab) +
+    stat_summary(fun.data = "mean_cl_boot") + 
+    stat_summary(fun.y = mean, geom = "line") + 
+    geom_hline(yintercept=0.125) + 
+    theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
+    ylab("Accuracy") + 
+    ylim(0,1)+
+    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,2,4,8,16,64),labels = c("1","2","4","8","16","64"), trans = "log2") + 
+    theme(plot.title = element_text(hjust = 0.5))
+  
+}
+
 plot_fig4 <- function(restspd, ggtit) {
   df_exp2a %>%
     filter(restk == restspd) %>%

### 2018-09-25 R/manuscript_app.Rmd
fig 3 in function

@@
 ```{r Figure 3a}
-df_exp1b %>% 
-  ggplot(aes(x = targetk, y = accuracy) + 
-    facet_grid(~restk, 
-               labeller = labeller(
-        xfacet = c(`2` = expression("Target's"~kappa~"=2"), 
-                   `4` = expression("Target's"~kappa~"=4"),
-                   `8` = expression("Target's"~kappa~"=8"),
-                   `16` = expression("Target's"~kappa~"=16"),
-                   `64` = expression("Target's"~kappa~"=64"))
 
-    )) +
-    stat_summary(fun.data = "mean_cl_boot") + 
-    stat_summary(fun.y = mean, geom = "line") + 
-    geom_hline(yintercept=0.125) + 
-    theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
-    ylab("Accuracy") + 
-    ylim(0,1)+
-    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,2,4,8,16,32,64,128),labels = c("1","2","4","8","16","32","64","128"), trans = "log2") + 
-    geom_vline(xintercept = restk_var, linetype = 2) +
-    ggtitle(ggtit) +
-    theme(plot.title = element_text(hjust = 0.5))
+p <- plot_fig3b()  
+p
+
+ggsave(file.path(plot_pth, "Figure3b.png"), p, width = 12, height = 6)
+
 ```

### 2018-10-03 R/manuscript_app.Rmd
update analysis regarding exp 2

@@
         wid = subject,
-        within = type, 
+        within = as.type, 
         detailed = T) %>% 

### 2018-10-03 R/tools.R

@@ -110,7 +110,7 @@ plot_fig3 <- function(restk_var, show_legend = F) {
   
 }
 
-plot_fig3b <- function() {
+plot_fig3a <- function() {
   restk_lab <- as_labeller(c(`2` = expression("Distractor's"~kappa~"=2"), 
                              `4` = expression("Distractor's"~kappa~"=4"),
                              `8` = expression("Distractor's"~kappa~"=8"),
@@ -127,7 +127,7 @@ plot_fig3b <- function() {
     ylim(0,1)+
     scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,2,4,8,16,64),labels = c("1","2","4","8","16","64"), trans = "log2") + 
     theme(plot.title = element_text(hjust = 0.5))
-  
+  p
 }
 
 plot_fig4 <- function(restspd, ggtit) {
@@ -158,6 +158,45 @@ plot_fig5 <- function(restspd, show_legend = F) {
     scale_x_continuous("Variable speed (log scale)",breaks = c(.5,1,2,4,8),labels = c(".5","1","2","4","8"),
                        trans = "log2") + 
     geom_vline(xintercept = restspd, linetype = 2) +
+    ggtitle(bquote("Fixed speed = "~.(restspd)*degree*"/s"))
+  if (show_legend) {
+    p 
+  } else {
+    p + theme(legend.position="none")
+  }   
+}
+
+plot_fig5b <- function(restspd, show_legend = F) {
+  restk_lab <- as_labeller(c(`2` = expression("Distractor's"~kappa~"=2"), 
+                             `4` = expression("Distractor's"~kappa~"=4"),
+                             `8` = expression("Distractor's"~kappa~"=8"),
+                             `16` = expression("Distractor's"~kappa~"=16"),
+                             `64` = expression("Distractor's"~kappa~"=64")), label_parsed)
+  p <- df_exp1b %>% 
+    ggplot(aes(x = targetk, y = accuracy)) + 
+    facet_grid(~restk, labeller = restk_lab) +
+    stat_summary(fun.data = "mean_cl_boot") + 
+    stat_summary(fun.y = mean, geom = "line") + 
+    geom_hline(yintercept=0.125) + 
+    theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
+    ylab("Accuracy") + 
+    ylim(0,1)+
[…]

### 2018-10-06 R/manuscript_app.Rmd
changes with manuscript revision

@@
   filter(block != 0) %>% as_tibble(.) %>% 
-  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
+  rename(tagetspd = type) %>% mutate(id = factor(subject)) %>% 
   mutate(contrast_abs = abs(log2(targetk / restk)), 
@@
 ```{r exp 2b - load data}
-df_exp2b <- readRDS(here::here("..", "data", "exp2b", "responses", "responses_171023.rds")) %>% 
- filter(block != 0)
-
-df_exp2b <- df_exp2b %>% mutate(restk = restk * 100, type = type * 100)
+df_exp2b <- 
+  readRDS(
+    file.path(data_pth, "exp2b", "responses", "responses_171023.rds")) %>% 
+  filter(block != 0) %>% as_tibble(.) %>% 
+  rename(targetspd = type, restspd = restk) %>% 
+  mutate(id = factor(subject)) %>% 
+  mutate(restspd = restspd * 100, targetspd = targetspd * 100) %>% 
+  mutate(contrast_abs = abs(log2(targetspd / restspd)), 
+         target_faster = (targetspd > restspd),
+         ratio = (besselI(restspd,0) * exp(targetspd)) / (besselI(targetspd,0) * exp(restspd)),
+         ratio_abs = abs(log((besselI(restspd,0) * exp(targetspd))) / (besselI(targetspd,0) * exp(restspd))),
+         ratio_abs = abs(log((besselI(restspd,0) * exp(targetspd))) / (besselI(targetspd,0) * exp(restspd))))
 
@@
 
-df2_exp2b <- rbind(df_exp2b, df_exp2b)
-df2_exp2b$version <- 2
-df2_exp2b$version[1:nrow(df_exp2b)] <- 1
-
-# this is a little hack, just to make a correct ggplot with one line
-tmp <- df_exp2b$restk
-df2_exp2b$restk[df2_exp2b$version == 2] <- df_exp2b$type
-df2_exp2b$type[df2_exp2b$version == 2] <- tmp
-
-df2_exp2b$version <- factor(df2_exp2b$version, labels = c("fix distractors' speed", "fix target's speed"))
+# df2_exp2b <- rbind(df_exp2b, df_exp2b)
+# df2_exp2b$version <- 2
+# df2_exp2b$version[1:nrow(df_exp2b)] <- 1
+# 
+# # this is a little hack, just to make a correct ggplot with one line
+# tmp <- df_exp2b$restk
+# df2_exp2b$restk[df2_exp2b$version == 2] <- df_exp2b$type
+# df2_exp2b$type[df2_exp2b$version == 2] <- tmp
+# 
+# df2_exp2b$version <- factor(df2_exp2b$version, labels = c("fix distractors' speed", "fix target's speed"))
 ```
@@
 
+## Descriptive statistics
+
+```{r accuracy for speed differences }
+
+df_exp2b %>% filter(abs(targetspd-restspd) >= 1) %>% summarize(m = mean(accuracy), sd = sd(accuracy)) %>% knitr::kable(digits = 2)
+
+```
+
 ## Figure 5
@@
 
-p_sp05 <- plot_fig5(0.5)
-p_sp1 <- plot_fig5(1)
-p_sp2 <- plot_fig5(2)
-p_sp4 <- plot_fig5(4)
-p_sp8 <- plot_fig5(8)
-p_sp8_legend <- plot_fig5(8, show_legend = T)
+p_sp05 <- plot_fig5b(0.5)
+p_sp1 <- plot_fig5b(1)
+p_sp2 <- plot_fig5b(2)
+p_sp4 <- plot_fig5b(4)
+p_sp8 <- plot_fig5b(8)
+#p_sp8_legend <- plot_fig5(8, show_legend = T)
 
 gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 3)
-ggsave(file.path(plot_pth, "Fig5_sp05.eps"), p_sp05, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp1.eps"), p_sp1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp2.eps"), p_sp2, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp4.eps"), p_sp4, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp8.eps"), p_sp8, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp8_legend.eps"), p_sp8_legend, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5b_sp05.eps"), p_sp05, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5b_sp1.eps"), p_sp1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5b_sp2.eps"), p_sp2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5b_sp4.eps"), p_sp4, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig5b_sp8.eps"), p_sp8, width = 6, height = 6)
+
 # final plot was created in inkscape
@@
 
+## Figure 6
+
+```{r}
+
+accu_summary <- df_exp2b %>% 
+  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
+  group_by(id, contrast_abs, contrast_abs_f, target_faster) %>% 
+  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
+  ungroup()
+accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)
+
+# duplicated values for contrast 0
+accu_summaryx <- bind_rows(
+  accu_summary,
+  accu_summary %>% 
+    filter(contrast_abs == 0, target_faster == F) %>% 
+    mutate(target_faster = T)
+)
+
+p <- accu_summaryx %>% 
+  ggplot(
+    aes(x = contrast_abs, y = accu, 
+        group = target_faster, shape = target_faster, linetype = target_faster)) + 
+  stat_summary(fun.data = "mean_cl_boot", alpha = .5, linetype = "solid") +
+  stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
+  theme(aspect.ratio = 1) + 
+  scale_shape_discrete("Distractor type", labels = c("Faster then target", "Slower than target")) +
+  scale_linetype_discrete("Distractor type", labels = c("Faster then target", "Slower than target")) +
+  xlab("contrast") + ylab("Accuracy")
+p
+ggsave(file.path(plot_pth, "Figure6.png"), p, width = 9, height = 6)
+
+```
+
 ## Compute the asymmetry
+
+```{r exp2b - tests}
+accu_summaryx %>%
+  filter(contrast_abs!=0) %>% 
+  group_by(contrast_abs) %>% 
+  do(ez::ezANOVA(., dv = accu, wid = id, within = target_faster, detailed = T)$ANOVA) %>% 
+  filter(Effect != "(Intercept)") %>% 
+  mutate(p = round(p, 3), ges = round(ges,2), F = round(F,1)) %>% 
+  transmute(`Contrast level` = contrast_abs, `F(1,15)`=F,p, ges) %>% 
+  knitr::kable()
+```
 

### 2018-10-06 R/tools.R

@@ -167,42 +167,22 @@ plot_fig5 <- function(restspd, show_legend = F) {
 }
 
 plot_fig5b <- function(restspd, show_legend = F) {
-  restk_lab <- as_labeller(c(`2` = expression("Distractor's"~kappa~"=2"), 
-                             `4` = expression("Distractor's"~kappa~"=4"),
-                             `8` = expression("Distractor's"~kappa~"=8"),
-                             `16` = expression("Distractor's"~kappa~"=16"),
-                             `64` = expression("Distractor's"~kappa~"=64")), label_parsed)
-  p <- df_exp1b %>% 
-    ggplot(aes(x = targetk, y = accuracy)) + 
-    facet_grid(~restk, labeller = restk_lab) +
-    stat_summary(fun.data = "mean_cl_boot") + 
-    stat_summary(fun.y = mean, geom = "line") + 
-    geom_hline(yintercept=0.125) + 
-    theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
-    ylab("Accuracy") + 
-    ylim(0,1)+
-    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,2,4,8,16,64),labels = c("1","2","4","8","16","64"), trans = "log2") + 
-    theme(plot.title = element_text(hjust = 0.5))
-  p
-  
+   
   p <- df_exp2b %>%
+    filter(restk == restspd) %>% 
     ggplot(aes(x = type, y = accuracy,xintercept = restk)) + 
-    facet_grid(~restk) +
     stat_summary(fun.data = "mean_cl_boot") + 
     stat_summary(fun.y = mean, geom = "line") + 
     geom_hline(yintercept=0.125) +
     theme(aspect.ratio = 1) + 
     ylab("Accuracy") + 
     ylim(0,1)+
-    scale_x_continuous("Variable speed (log scale)",breaks = c(.005,.01,.02,.04,.08),labels = c("0.5","1","2","4","8"),
+    scale_x_continuous("Target speed (log scale)",breaks = c(.5,1,2,4,8),labels = c("0.5","1","2","4","8"),
                        trans = "log2") + 
-    geom_vline(aes(xintercept = restk), linetype = 2) +
-    ggtitle(bquote("Fixed speed = "~.(restspd)*degree*"/s"))
-  if (show_legend) {
-    p 
-  } else {
-    p + theme(legend.position="none")
[…]

### 2018-10-10 R/manuscript_app.Rmd
make Figure separately, not by faceting

--- 2018-10-03 R/manuscript_app.Rmd
@@
 
-```{r Figure 3a}
+```{r}
+p_k2 <- plot_fig3(2)
+p_k4 <- plot_fig3(4)
+p_k8 <- plot_fig3(8)
+p_k16 <- plot_fig3(16)
+p_k64 <- plot_fig3(64)
+p_k64_legend <- plot_fig3(64, show_legend = T)
 
-p <- plot_fig3b()  
-p
-
-ggsave(file.path(plot_pth, "Figure3b.png"), p, width = 12, height = 6)
-
+gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
+ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
+# final plot was created in inkscape
 ```
@@
 ```
-
-# Appendix
-
-```{r}
-#p_k2 <- plot_fig3(2)
-#p_k4 <- plot_fig3(4)
-#p_k8 <- plot_fig3(8)
-#p_k16 <- plot_fig3(16)
-#p_k64 <- plot_fig3(64)
-#p_k64_legend <- plot_fig3(64, show_legend = T)
-
-#gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
-#ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
-#ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
-#ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
-#ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
-#ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
-#ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
-# final plot was created in inkscape
-```

### 2018-10-10 R/tools.R

@@ -86,7 +86,7 @@ plot_fig2 <- function(restk_var, ggtit) {
 
 plot_fig3 <- function(restk_var, show_legend = F) {
   
-  p <- df2_exp1b %>%
+  p <- df_exp1b %>%
     filter(restk == restk_var) %>%
     ggplot(aes(x = type, y = accuracy, group = version)) + 
     #facet_grid(~ restk) + 
@@ -96,8 +96,7 @@ plot_fig3 <- function(restk_var, show_legend = F) {
     theme(aspect.ratio = 1) + 
     ylab("Accuracy") + 
     ylim(0,1)+
-    scale_x_continuous(expression("Variable"~kappa~" (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
-    scale_linetype_manual(values = c(2,1)) +
+    scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
     geom_vline(xintercept = restk_var, linetype = 2) +
     ggtitle(bquote("Fixed "~kappa~"= "~.(restk_var))) +
     theme(plot.title = element_text(hjust = 0.5))

### 2018-10-12 R/tools.R
change figure 3

@@ -75,7 +75,8 @@ plot_fig2 <- function(restk_var, ggtit) {
     stat_summary(fun.data = "mean_cl_boot") + 
     stat_summary(fun.y = mean, geom = "line", aes(group = 1)) + 
     geom_hline(yintercept=0.125) + 
-    theme(aspect.ratio = 1)  + xlab(expression("Target's"~kappa)) + 
+    theme(aspect.ratio = 1) + 
+    xlab(expression("Target's"~kappa)) + 
     ylab("Accuracy") + 
     ylim(0,1)+
     scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(1,2,4,8,16,32,64,128),labels = c("1","2","4","8","16","32","64","128"), trans = "log2") + 
@@ -88,17 +89,17 @@ plot_fig3 <- function(restk_var, show_legend = F) {
   
   p <- df_exp1b %>%
     filter(restk == restk_var) %>%
-    ggplot(aes(x = type, y = accuracy, group = version)) + 
+    ggplot(aes(x = type, y = accuracy, group = 1)) + 
     #facet_grid(~ restk) + 
     stat_summary(fun.data = "mean_cl_boot") + 
-    stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
+    stat_summary(fun.y = mean, geom = "line") + 
     geom_hline(yintercept=0.125) +
     theme(aspect.ratio = 1) + 
     ylab("Accuracy") + 
     ylim(0,1)+
     scale_x_continuous(expression("Target's"~kappa~" (log scale)"),breaks = c(2,4,8,16,64),labels = c("2","4","8","16","64"), trans = "log2") + 
     geom_vline(xintercept = restk_var, linetype = 2) +
-    ggtitle(bquote("Fixed "~kappa~"= "~.(restk_var))) +
+    ggtitle(bquote("Distractors'"~kappa == .(restk_var))) +
     theme(plot.title = element_text(hjust = 0.5))
   
   if (show_legend) {

### 2018-10-16 R/manuscript_app.Rmd
compute average accuracy for speed differences
polish code for review

--- 2018-10-10 R/manuscript_app.Rmd
@@
 date: '`r format(Sys.time(), "%d %B, %Y")`'
-output: html_document
+output:
+  word_document: default
+  html_document: default
 ---
@@
 
-```{r Figure 1}
+Created by script *generate_vonmises_example*
+
+## Figure 2
+
+```{r Figure 2}
 traj_k64 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_64_rest4.csv")) %>% select(x = V1,y = V2) %>% as_data_frame()
@@
 
-ggsave(file.path(plot_pth, "Figure1_ballistic.png"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure1_brownian.png"), p2, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure1_ballistic.eps"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure1_brownian.eps"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure2_ballistic.png"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure2_brownian.png"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure2_ballistic.eps"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure2_brownian.eps"), p2, width = 6, height = 6)
 ```
 
-## Figure 2
+## Figure 3
 
-```{r Figure 2}
+```{r Figure 3}
 
-p1 <- plot_fig2(4, "Brownian-like-distractors")
-p2 <- plot_fig2(16, "Ballistic-like-distractors")
+p1 <- plot_fig3(4, "Brownian-like-distractors")
+p2 <- plot_fig3(16, "Ballistic-like-distractors")
 
@@
 
-ggsave(file.path(plot_pth, "Figure2_brownian.png"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure2_ballistic.png"), p2, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure2_brownian.eps"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure2_ballistic.eps"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure3_brownian.png"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure3_ballistic.png"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure3_brownian.eps"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure3_ballistic.eps"), p2, width = 6, height = 6)
 ```
@@
 
-## Figure 3a
+## Figure 4
 
-```{r}
-p_k2 <- plot_fig3(2)
-p_k4 <- plot_fig3(4)
-p_k8 <- plot_fig3(8)
-p_k16 <- plot_fig3(16)
-p_k64 <- plot_fig3(64)
-p_k64_legend <- plot_fig3(64, show_legend = T)
+```{r Figure 4}
+p_k2 <- plot_fig4(2)
+p_k4 <- plot_fig4(4)
+p_k8 <- plot_fig4(8)
+p_k16 <- plot_fig4(16)
+p_k64 <- plot_fig4(64)
+p_k64_legend <- plot_fig4(64, show_legend = T)
 
 gridExtra::grid.arrange(p_k2,p_k4, p_k8, p_k16, p_k64, ncol = 3)
-ggsave(file.path(plot_pth, "Fig3_k2.eps"), p_k2, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k4.eps"), p_k4, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k8.eps"), p_k8, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k16.eps"), p_k16, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k64.eps"), p_k64, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig3_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig4_k2.eps"), p_k2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig4_k4.eps"), p_k4, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig4_k8.eps"), p_k8, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig4_k16.eps"), p_k16, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig4_k64.eps"), p_k64, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig4_k64_legend.eps"), p_k64_legend, width = 6, height = 6)
 # final plot was created in inkscape
@@
 
-## Figure 3b
+## Figure 5
 
-```{r Figure 3b}
-accu_summary <- df_exp1b %>% 
-  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
-  group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
-  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
-  ungroup()
-accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)
+```{r Figure 5}
 
-# duplicated values for contrast 0
-accu_summaryx <- bind_rows(
-  accu_summary,
-  accu_summary %>% 
-    filter(contrast_abs == 0, target_straight == F) %>% 
-    mutate(target_straight = T)
-)
+p <- plot_fig5()
+ggsave(file.path(plot_pth, "Figure5.png"), p, width = 9, height = 6)
+```
 
-p <- accu_summaryx %>% 
-  ggplot(
-    aes(x = contrast_abs, y = accu, 
-        group = target_straight, shape = target_straight, linetype = target_straight)) + 
-  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
-  stat_summary(fun.y = "mean", alpha = .5, geom = "line") + 
-  theme(aspect.ratio = 1) + 
-  scale_shape_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
-  scale_linetype_discrete("Distractor type", labels = c("More Ballistic-like", "More Brownian-like")) +
-  xlab("contrast") + ylab("Accuracy")
-p
-ggsave(file.path(plot_pth, "Figure3.png"), p, width = 9, height = 6)
+## Table 1
+
+```{r Table 1, warning=F, message=F}
+df_exp1b %>% 
+  filter(contrast_abs > 0) %>% 
+  group_by(contrast_abs) %>% 
+  do(ez::ezANOVA(data = ., dv = accuracy, within = .(target_straight), wid = id)$ANOVA) %>% 
+  ungroup() %>% 
+  transmute(`Contrast level` = contrast_abs, `F(1,16)` = F, p = round(p, 3), ges = round(ges,2)) %>% 
+  knitr::kable(caption = "Results of within-subject ANCOVAs for each contrast level for movement variability")
 ```
@@
 
-```{r exp 1b - compute the assymetry, warning=F}
+```{r exp 1b - compute the assymetry, warning=F,eval = FALSE}
 df3_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(p=compute.p(.))
@@
 df_exp1b %>% 
-  group_by(type, restk, subject) %>% 
-  summarize(accuracy = mean(accuracy)) %>% group_by(restk, type) %>%
+  group_by(targetk, restk, subject) %>% 
+  summarize(accuracy = mean(accuracy)) %>% group_by(restk, targetk) %>%
   filter(accuracy < 1) %>% 
@@
   knitr::kable()
-```
-
-## Table 1
-
-```{r exp 1b - Table 1}
-df_exp1b %>% 
-  filter(restk == 2) %>% 
-  ez::ezANOVA(dv = accuracy,
-        wid = subject,
-        within = type, 
-        detailed = T) %>% 
-  apa::anova_apa()
-
-df_exp1b %>% 
-  filter(restk == 4) %>% 
-  ez::ezANOVA(dv = accuracy,
-        wid = subject,
-        within = type, 
-        detailed = T) %>% 
-  apa::anova_apa()
-df_exp1b %>% 
-  filter(restk == 8) %>% 
-  ez::ezANOVA(dv = accuracy,
-        wid = subject,
-        within = type, 
-        detailed = T) %>% 
-  apa::anova_apa()
-
-df_exp1b %>% 
-  filter(restk == 16) %>% 
-  ez::ezANOVA(dv = accuracy,
-        wid = subject,
-        within = type, 
-        detailed = T) %>% 
-  apa::anova_apa()
-
 ```
@@
   ez::ezANOVA(dv = accuracy,
-        wid = subject,
-        within = as.type, 
+        wid = as.factor(subject),
+        within = type, 
         detailed = T) %>% 
@@
         wid = as.factor(subject),
-        within = as.factor(type), 
+        within = type, 
         detailed = T) %>% 
@@
 
-### Figure 4
+### Figure 6
 
-```{r Figure 4}
+```{r Figure 6}
 
-p1 <- plot_fig4(2, ggtit = "Slow-moving-distractors")
+p1 <- plot_fig6(2, ggtit = "Slow-moving-distractors")
 
-p2 <- plot_fig4(4, ggtit = "Fast-moving-distractors")
+p2 <- plot_fig6(4, ggtit = "Fast-moving-distractors")
 
@@
 
-ggsave(file.path(plot_pth, "Figure4_slow.png"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure4_fast.png"), p2, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure4_slow.eps"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure4_fast.eps"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure6_slow.png"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure6_fast.png"), p2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure6_slow.eps"), p1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Figure6_fast.eps"), p2, width = 6, height = 6)
 ```
@@
 
-df2_exp2b <- rbind(df_exp2b, df_exp2b)
-df2_exp2b$version <- 2
-df2_exp2b$version[1:nrow(df_exp2b)] <- 1
-
-# this is a little hack, just to make a correct ggplot with one line
-tmp <- df_exp2b$restk
-df2_exp2b$restk[df2_exp2b$version == 2] <- df_exp2b$type
-df2_exp2b$type[df2_exp2b$version == 2] <- tmp
-
-df2_exp2b$version <- factor(df2_exp2b$version, labels = c("fix distractors' speed", "fix target's speed"))
 ```
@@
 
-## Figure 5
+## Descriptive statistics
 
-```{r Figure 5}
+```{r accuracy for speed differences }
 
-p_sp05 <- plot_fig5(0.5)
-p_sp1 <- plot_fig5(1)
-p_sp2 <- plot_fig5(2)
-p_sp4 <- plot_fig5(4)
-p_sp8 <- plot_fig5(8)
-p_sp8_legend <- plot_fig5(8, show_legend = T)
+df_exp2b %>% filter(abs(targetspd-restspd) >= 1) %>% summarize(m = mean(accuracy), sd = sd(accuracy)) %>% knitr::kable(digits = 2)
+
+df_exp2b %>% filter(contrast_abs >= 2, target_faster== F) %>% summarize(m = mean(accuracy), sd = sd(accuracy)) %>% knitr::kable(digits = 2)
+
+```
+
+## Figure 7
+
+```{r Figure 7}
+
+p_sp05 <- plot_fig7(0.5)
+p_sp1 <- plot_fig7(1)
+p_sp2 <- plot_fig7(2)
+p_sp4 <- plot_fig7(4)
+p_sp8 <- plot_fig7(8)
+#p_sp8_legend <- plot_fig5(8, show_legend = T)
 
 gridExtra::grid.arrange(p_sp05,p_sp1, p_sp2, p_sp4, p_sp8, ncol = 3)
-ggsave(file.path(plot_pth, "Fig5_sp05.eps"), p_sp05, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp1.eps"), p_sp1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp2.eps"), p_sp2, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp4.eps"), p_sp4, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp8.eps"), p_sp8, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Fig5_sp8_legend.eps"), p_sp8_legend, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig7_sp05.eps"), p_sp05, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig7_sp1.eps"), p_sp1, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig7_sp2.eps"), p_sp2, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig7_sp4.eps"), p_sp4, width = 6, height = 6)
+ggsave(file.path(plot_pth, "Fig7_sp8.eps"), p_sp8, width = 6, height = 6)
+
 # final plot was created in inkscape
+```
+
+## Figure 8
+
+```{r}
+
+p <- plot_fig8()
+ggsave(file.path(plot_pth, "Figure8.png"), p, width = 9, height = 6)
+
+```
+
+## Table 2
+
+```{r exp2b - Table 2}
+df_exp2b %>% 
+  filter(contrast_abs > 0) %>% 
+  group_by(contrast_abs) %>% 
+  do(ez::ezANOVA(data = ., dv = accuracy, within = .(target_faster), wid = id)$ANOVA) %>% 
+  ungroup() %>% 
+  transmute(`Contrast level` = contrast_abs, `F(1,15)` = F, p = round(p, 3), ges = round(ges,2)) %>% 
+  knitr::kable()
+
 ```
@@
 
-```{r exp 2b - compute the assymetry, warning=F}
+```{r exp 2b - compute the assymetry, warning=F,eval = FALSE}
 df3_exp2b <- df2_exp2b %>% group_by(type, restk) %>% do(p=compute.p(.))

### 2018-10-16 R/tools.R

@@ -68,7 +68,7 @@ compute.des <- function(dfx) {
   
 }
 
-plot_fig2 <- function(restk_var, ggtit) {
+plot_fig3 <- function(restk_var, ggtit) {
   df_exp1a %>%
     filter(restk == restk_var) %>%
     ggplot(aes(x = type, y = accuracy)) + 
@@ -85,11 +85,11 @@ plot_fig2 <- function(restk_var, ggtit) {
     theme(plot.title = element_text(hjust = 0.5))
 }
 
-plot_fig3 <- function(restk_var, show_legend = F) {
+plot_fig4 <- function(restk_var, show_legend = F) {
   
   p <- df_exp1b %>%
     filter(restk == restk_var) %>%
-    ggplot(aes(x = type, y = accuracy, group = 1)) + 
+    ggplot(aes(x = targetk, y = accuracy, group = 1)) + 
     #facet_grid(~ restk) + 
     stat_summary(fun.data = "mean_cl_boot") + 
     stat_summary(fun.y = mean, geom = "line") + 
@@ -130,7 +130,7 @@ plot_fig3a <- function() {
   p
 }
 
-plot_fig4 <- function(restspd, ggtit) {
+plot_fig6 <- function(restspd, ggtit) {
   df_exp2a %>%
     filter(restk == restspd) %>%
     ggplot(aes(x = type, y = accuracy)) + 
@@ -145,32 +145,39 @@ plot_fig4 <- function(restspd, ggtit) {
     ggtitle(ggtit)
 }
 
-plot_fig5 <- function(restspd, show_legend = F) {
-  p <- df2_exp2b %>%
-    filter(restk == restspd) %>%
-    ggplot(aes(x = type, y = accuracy, group = version)) + 
-    stat_summary(fun.data = "mean_cl_boot") + 
-    stat_summary(fun.y = mean, geom = "line", aes(group = version, linetype = version)) + 
-    geom_hline(yintercept=0.125) +
+plot_fig5 <- function() {
+  accu_summary <- df_exp1b %>% 
+    mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
+    group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
+    dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
+    ungroup()
+  accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)
+  
+  # duplicated values for contrast 0
[…]

### 2018-10-17 R/generate_vonmises_example.R
move Figure 2 to the main script

@@ -25,46 +25,7 @@ ggsave(here::here("..", "plots", "scheme_vonmises_k64.png"), p3, width = 6, heig
 
 # real data ---------------------------------------------------------------
 
-data_pth <- here::here("..","data", "exp1b", "trajectories")
 
-traj_k64_raw <- read.table(file.path(data_pth, "T001_4_rest64.csv")) %>% 
-  as_data_frame() %>% 
-  mutate(t=1:n())
-
-trajx <- traj_k64_raw %>% 
-  select(V1,V3,V5,V7,V9,V11,V13,V15,t) %>% 
-  gather(key = "object", value = "xcoord", -t) %>% 
-  mutate(object = recode(object, V1 = "o1", V3 = "o2", V5 = "o3", V7 = "o4", V9 = "o5", V11 = "o6", V13 = "o7", V15 = "o8"))
-
-trajy <- traj_k64_raw %>% 
-  select(V2,V4,V6,V8,V10,V12,V14,V16,t) %>% 
-  gather(key = "object", value = "ycoord", -t) %>% 
-  mutate(object = recode(object, V2 = "o1", V4 = "o2", V6 = "o3", V8 = "o4", V10 = "o5", V12 = "o6", V14 = "o7", V16 = "o8"))
-
-traj_k64 <- trajx %>% 
-  left_join(trajy, by = c("t", "object")) %>% 
-  mutate(type = if_else(object == "o1", "target", "distractor"))
-  
-  
-p <- traj_k64 %>% 
-  filter(t > 10) %>%
-  filter(object %in% c("o1","o2","o7","o3","o5")) %>% 
-  ggplot(aes(xcoord, ycoord, group = object)) + 
-  geom_path(size = 0.5) + 
-  theme(aspect.ratio = 1) + 
-  xlim(-15,15) +
-  ylim(-15,15) +
-  #scale_linetype_manual(values=c("solid", "solid")) + 
-  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o2","o7","o3","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
-  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o1")), aes(xcoord, ycoord, fill = type), size = 4, shape = 1, show.legend=FALSE) +
[…]

### 2018-10-17 R/manuscript_app.Rmd
additional changes to the manuscript

@@
 ```{r Figure 2}
-traj_k64 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_64_rest4.csv")) %>% select(x = V1,y = V2) %>% as_data_frame()
-p1 <- traj_k64 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15) +
-  ggtitle("Ballistic-like")
+data_pth <- here::here("..","data", "exp1b", "trajectories")
 
-traj_k4 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_4_rest4.csv")) %>% select(x = V3,y = V4) %>% as_data_frame()
-p2 <- traj_k4 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15)+
-  ggtitle("Brownian-like")
-gridExtra::grid.arrange(p1,p2, ncol = 2)
+traj_k64_raw <- read.table(file.path(data_pth, "T001_4_rest64.csv")) %>% 
+  as_data_frame() %>% 
+  mutate(t=1:n())
 
-ggsave(file.path(plot_pth, "Figure2_ballistic.png"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure2_brownian.png"), p2, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure2_ballistic.eps"), p1, width = 6, height = 6)
-ggsave(file.path(plot_pth, "Figure2_brownian.eps"), p2, width = 6, height = 6)
+trajx <- traj_k64_raw %>% 
+  select(V1,V3,V5,V7,V9,V11,V13,V15,t) %>% 
+  gather(key = "object", value = "xcoord", -t) %>% 
+  mutate(object = recode(object, V1 = "o1", V3 = "o2", V5 = "o3", V7 = "o4", V9 = "o5", V11 = "o6", V13 = "o7", V15 = "o8"))
+
+trajy <- traj_k64_raw %>% 
+  select(V2,V4,V6,V8,V10,V12,V14,V16,t) %>% 
+  gather(key = "object", value = "ycoord", -t) %>% 
+  mutate(object = recode(object, V2 = "o1", V4 = "o2", V6 = "o3", V8 = "o4", V10 = "o5", V12 = "o6", V14 = "o7", V16 = "o8"))
+
+traj_k64 <- trajx %>% 
+  left_join(trajy, by = c("t", "object")) %>% 
+  mutate(type = if_else(object == "o1", "target", "distractor"))
+
+p1 <- traj_k64 %>% 
+  filter(t > 10) %>%
+  filter(object %in% c("o1","o2","o7","o3","o5")) %>% 
+  ggplot(aes(xcoord, ycoord, group = object)) + 
+  geom_path(size = 0.5) + 
+  theme(aspect.ratio = 1) + 
+  xlim(-15,15) +
+  ylim(-15,15) +
+  #scale_linetype_manual(values=c("solid", "solid")) + 
+  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o2","o7","o3","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
+  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o1")), aes(xcoord, ycoord, fill = type), size = 4, shape = 1, show.legend=FALSE) +
+  #geom_point(data = traj_k64 %>% filter(t==max(t),object %in% c("o1","o2","o7","o4","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
+  guides(color = FALSE) +
+  xlab("x [deg]") +
+  ylab("y [deg]") +
+  ggtitle(expression("Target's "*kappa~"= 4; Distractors' "*kappa~"= 64")) +
+  theme(plot.title = element_text(hjust = 0.5))
+p1
+ggsave(here::here("..", "plots", "Figure2.png"), p1, width = 6, height = 6)
+
+ggsave(here::here("..", "plots", "Figure2_t1.eps"), plot_trial_frame(t = 1), width = 6, height = 6)
+
+maxt <- traj_k64$t %>% max()
+
+ggsave(here::here("..", "plots", "Figure2_tmax.eps"), plot_trial_frame(t = maxt), width = 6, height = 6)
+
+# final version was adjusted in inkscape 
 ```
@@
   knitr::kable()
+```
+
+## Reaction times
+
+```{r}
+df_exp1a %>% 
+  group_by(restk2) %>% 
+  filter(accuracy == 1) %>% 
+  lmerTest::lmer(responseTime~type+(1|subject),.) %>% lmerTest::summary() %>% broom::tidy()
+
 ```

### 2018-10-17 R/tools.R

@@ -85,6 +85,25 @@ plot_fig3 <- function(restk_var, ggtit) {
     theme(plot.title = element_text(hjust = 0.5))
 }
 
+plot_trial_frame <-function(tt) {
+  traj_k64 %>% 
+    filter(t == tt) %>%
+    ggplot(aes(xcoord, ycoord, group = object)) + 
+    geom_point(size = 5) + 
+    theme(aspect.ratio = 1) + 
+    xlim(-15,15) +
+    ylim(-15,15) +
+    theme(panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          panel.background = element_blank(), 
+          axis.title.x=element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank(),
+          axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
+}
+
 plot_fig4 <- function(restk_var, show_legend = F) {
   
   p <- df_exp1b %>%

### 2018-12-05 R/generate_video_example.R
generate video trajectory
code adjusted from Jiri's gist

@@ -1,0 +1,156 @@
+library(tidyverse)
+library(animation)
+library(circular)
+
+
+data_pth <- here::here("..","data", "exp1b", "trajectories")
+
+traj_k64_raw <- read.table(file.path(data_pth, "T001_4_rest64.csv")) %>% 
+  as_data_frame() %>% 
+  mutate(t=1:n())
+
+trajx <- traj_k64_raw %>% 
+  select(V1,V3,V5,V7,V9,V11,V13,V15,t) %>% 
+  gather(key = "object", value = "xcoord", -t) %>% 
+  mutate(object = recode(object, V1 = "o1", V3 = "o2", V5 = "o3", V7 = "o4", V9 = "o5", V11 = "o6", V13 = "o7", V15 = "o8"))
+
+tt <- list()
+class(tt) <- "trajectory"
+tt$n <- 8
+tt$xlim <- c(-15,15)
+tt$ylim <- c(-15,15)
+tt$time <- seq(0,(nrow(traj_k64_raw)-1)/100, by = 0.01)
+x <- traj_k64_raw %>% select(V1,V3,V5,V7,V9,V11,V13,V15) %>% as.matrix()
+colnames(x) <- NULL
+y <- traj_k64_raw %>% select(V2,V4,V6,V8,V10,V12,V14,V16) %>% as.matrix()
+colnames(y) <- NULL
+
+tt$x <- x
+tt$y <- y
+
+# final version was adjusted in inkscape 
+
+# utility functions for trajectory generation -------------------
+#   - these function came from motAnalysis package 
+
+snapshot.trajectory <- function(track, time, time.index = NA) {
+  if (is.na(time.index)) {
+    time.index <- which.min(abs(track$time - time))
+  }
+  pos <- list(
+    n = track$n, xlim = track$xlim, ylim = track$ylim,
+    x = track$x[time.index, ],
+    y = track$y[time.index, ],
+    radius = 0.5
+  ) # TODO
+  class(pos) <- "positions"
+  return(pos)
+}
+
+
+
+# display functions ---------------------------------------------
+xplot.positions <- function(pos, targets = NA, labels = F,
+                            legend = F, expand = c(0, 1)) {
+  expand.add <- c(-1, +1) * expand[2]
+  expand <- as.numeric(na.omit(c(expand, 0, 0))) # add one or two zeros
+  width <- diff(pos$xlim)
+  height <- diff(pos$ylim)
+  margin.x <- width * expand[1]
+  margin.y <- height * expand[1]
[…]

### 2018-12-05 R/manuscript_app.Rmd

@@
   as_data_frame() %>% 
-  mutate(restk2 = recode(restk, `4` = "Brownian-like", `16` = "Ballistic-like"))
+  mutate(restk2 = recode(restk, `4` = "Brownian-like", `16` = "Ballistic-like")) %>% 
+  mutate(type2 = as.factor(type))
 
@@
 ggsave(here::here("..", "plots", "Figure2.png"), p1, width = 6, height = 6)
+ggsave(here::here("..", "plots", "Figure2.eps"), p1, width = 6, height = 6)
 
@@
         wid = subject,
-        within = type, 
-        detailed = T) %>% 
+        within = type2, 
+        detailed = T,) %>% 
   apa::anova_apa()
@@
 
-## Compute the asymmetry
-
-We run multiple within subject anova
-
-```{r exp 1b - compute the assymetry, warning=F,eval = FALSE}
-df3_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(p=compute.p(.))
-
-df3_exp1b$p <- unlist(df3_exp1b$p) %>% round(3)
-df4_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(ges=compute.des(.))
-df4_exp1b$ges <- unlist(df4_exp1b$ges) %>% round(2)
-df3_exp1b$ges <- df4_exp1b$ges
-
-df5_exp1b <- df2_exp1b %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
-  group_by(type, restk) %>%
-  summarize(acc_diff = accuracy[version == "fix distractors' k"] - accuracy[version == "fix target's k"])
-
-m <- matrix(df3_exp1b$ges, nrow = 5)
-rownames(m) <- levels(df_exp1b$type)
-colnames(m) <- levels(df_exp1b$type)
-m[upper.tri(m,diag = T)] <- NA
-
-df3_exp1b$ges <- as.vector(m)
-
-m <- matrix(df3_exp1b$p, nrow = 5)
-m[upper.tri(m, diag = T)] <- NA
-df3_exp1b$p <- as.vector(m)
-
-m <- matrix(df5_exp1b$acc_diff, nrow = 5)
-m[upper.tri(m, diag = T)] <- NA
-df3_exp1b$acc_diff <- as.vector(m)
-
-df3_exp1b$target_lower_than_dist <- df3_exp1b$acc_diff < 0
-df3_exp1b %>% filter(target_lower_than_dist)
-
-df3_exp1b %>% filter(p < .05)
-```
-
 ## Test with baseline
@@
   knitr::kable()
+```
+
+## Overall test
+
+```{r exp1b overtall test}
+
+df_exp1b %>% 
+  filter(contrast_abs!=0) %>% 
+  ezANOVA(dv = accuracy, within = .(contrast_abs, target_straight), wid = id,
+          detailed = T) %>% 
+  apa::anova_apa(sph_corr = "none", es = "ges")
+
 ```
@@
 
+## Overall test
+
+```{r exp2b overtall test}
+
+df_exp2b %>% 
+  filter(contrast_abs!=0) %>% 
+  ezANOVA(dv = accuracy, within = .(contrast_abs, target_faster), wid = id,
+          detailed = T) %>% 
+  apa::anova_apa(sph_corr = "none", es = "ges")
+
+```
+
 ## Table 2
